---
title: "VNI Analysis of RDM behavior"
author: "Hayley Brooks"
---

Tips/Tricks from template:
1) Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Cmd+Shift+Enter*. 
2) Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.
3) When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 
4) The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.



# Config
```{r}
library(config)
config::get()
```


Set up the environment
```{r}
rm(list=ls());  # clear environment
load("/Volumes/shlab/Projects/VNI/data/mriBehaviorClean/group_mriBehavior_clean.Rdata"); # load cleaned RDM dataset with Qualtrics responses
```


Subject information
```{r}
subIDs = unique(mriBehClean$subjectIndex);
nSub = length(subIDs);
print(nSub)
```
