---
title: "VNI Analysis of RDM behavior"
author: "Hayley Brooks"
output:
  #pdf_notebook: default
  html_notebook: default
---

##### Set up
```{r}
rm(list=ls());  # clear environment


library(config);
config <- config::get();

vni_csv = file.path(config$path$data$clean,config$csvs$RDM_group_clean_csv);
mriBehClean = read.csv(vni_csv);


library(lme4);
library(lmerTest);
```

***
##### Subject information
```{r}
subIDs = unique(mriBehClean$subjectIndex);
nSub = length(subIDs);
sprintf("N = %s", nSub)
```

***
### Big Question
#### Does risk-taking change as a function of temporal context at three levels?
1) Immediate (past outcome) 
2) Neighborhood (shifts) 
3) Global (earnings)


***

### Trial-level model
##### Summary: Participants more likely to choose an option as its amount increases (no effect of ground expected value)
```{r}
model1_trialLevel = glmer(choice~ 0 + gainSC + altSC + grndEVscaled + (0+ gainSC + altSC|subjectIndex), data = mriBehClean, family = "binomial"); # model identical to VIC

summary(model1_trialLevel);

```

***
#####  Pull out "predicted" values from trial-level model and save as variable "pred" in mriBehClean dataframe
**Using "offset", they'll be applied inside the softmax with a weight of 1 every time, in effect accounting for our best current-trial predictions by directly entering those predictions on a trial-by-trial level. This lets us retain the binomial analysis structure vs using residuals ("resids"), which is much more accurate.**

```{r}
mriBehClean$pred= predict(model1_trialLevel,type="link"); 
par(mfrow=c(1,1))
#plot(mriBehClean$pred, ylab="predicted values");

```

***
#### 1) Immediate timescale: past outcome  
##### Past outcome amount and type: past outcome and type alone in models both not significant. In a model with past outcome type, type is significant (beta = .12(.06), p=.03) and interacts with outcome amount (beta = -.54(.2), p=.005). The model with the interaction performs better by AIC comparison.
```{r}
model2_potc_amt = glmer(choice ~ 0 + poc1scaled + (1|subjectIndex), data=mriBehClean, family="binomial", offset=pred);
summary(model2_potc_amt);  # ns; AIC = 7592.9 

model2_potc_type = glmer(choice ~ 0 + poc1type + (1|subjectIndex), data=mriBehClean, family="binomial", offset=pred);
summary(model2_potc_type); # ns; AIC =7592.1 

model2_potc_amt_type_intxn = glmer(choice ~ 0 + poc1type*poc1scaled + (1|subjectIndex), data=mriBehClean, family="binomial", offset=pred);
summary(model2_potc_amt_type_intxn); # negative interaction between outcome type and amount; AIC = 7588.0

```

**Plot the interaction between past outcome amount and type:**  
**Outcome type is coded: 0 = safe; 1 = risky gain; -1 = risky loss (always $0)**
```{r}

m2coef = fixef(model2_potc_amt_type_intxn); # store all beta estimates

typeCoef = m2coef[1]; # past outcome type coefficient
amtCoef = m2coef[2]; # past outcome amount coefficient
intxnCoef = m2coef[3]; # past outcome type and amount interaction coefficient

## SAFE OUTCOMES
# Largest outcome when a participant rejected gamble = 30.49, scaled = .499918
# smallest outcome when a participant rejected gamble  = .78, scaled = .01278898
PgamPOCsafeSmall = 1/(1+exp(-1*( (typeCoef*0) + (amtCoef*.499918) + (intxnCoef*0*.499918) ))); 
# probability of gambling following a small, safe past outcome  = 0.5275424, 2.7% increase

PgamPOCsafeLarge = 1/(1+exp(-1*( (typeCoef*0) + (amtCoef*.01278898) + (intxnCoef*0*.01278898) ))); 
# probability of gambling following a large, safe past outcome  = 0.5007053 

## GAINS
# largest outcome when a participant accepted gamble and won = $60.99, scaled = 1
# smallest outcome when a participant accepted gamble and won = $5.31, scaled = 0.08706345
  # technically, the minimum it could be 0 if participants missed an attn check
# medium outcome = $30.5, scaled = .5
# outcome when a participant accepted gamble and lost = $0

PgamPOCwinLarge = 1/(1+exp(-1*( (typeCoef*1) + (amtCoef*1) + (intxnCoef*1*1) ))); 
# probability of gambling following a large, risky win = 0.4511035, 5% decrease 
PgamPOCwinSmall = 1/(1+exp(-1*( (typeCoef*1) + (amtCoef*0.08706345) + (intxnCoef*1*0.08706345) ))); 
# probability of gambling following a small, risky win = 0.5237715, a 2% increase
PgamPOCwinMedium = 1/(1+exp(-1*( (typeCoef*1) + (amtCoef*.5) + (intxnCoef*1*.5) ))); 
# probability of gambling following a medium, risky win = 0.4908425, a slight (<1%) decrease


## LOSSES (always zero)
PgamPOClossZero = 1/(1+exp(-1*( (typeCoef*-1) + (amtCoef*0) + (intxnCoef*-1*0) ))); 
# probability of gambling following a loss = 0.4693025, a 4.5% decrease


plot(c(PgamPOCwinSmall, PgamPOCwinMedium, PgamPOCwinLarge), type="l", col="green", lwd=3, ylim=c(0,1), main="Risk-taking as a function of past outcome type and amount", ylab="p(gamble)", xlab="past outcome", axes=F)
legend("topleft", legend=c("gain", "loss", "safe"), text.col = c("green", "red", "blue"), bty="n")
axis(2)
axis(1, labels=c("small", "medium", "large"), at=c(1,2,3))
lines(c(PgamPOCsafeSmall,PgamPOCsafeLarge), col="blue", lwd=3)
points(c(PgamPOClossZero), pch=16, col="red", lwd= 3)



```

It looks like there is a very slight difference between loss and gain/safe outcome. Do people treat losses like a missed gain? No, doesn't look like that is happening here.
```{r}
# Missed gain variable - positive value for losses (its the previous risky gain amount). Note that this is the missed gain on the previous trial.
model2_potc_missedGain_type_intxn = glmer(choice ~ 0 + pocMissedGain*poc1type+ (1|subjectIndex), data=mriBehClean, family="binomial", offset=pred);
summary(model2_potc_missedGain_type_intxn); #AIC = 7594.1, nothing is significant

# Another way to look at this would be a regressor that is received - not received (so it is one continuous regressor that includes losses(missed gains), wins, and safes on the previous trial). Don't need to include type here.
model2_potc_receivedDiff_type_intxn = glmer(choice ~ 0 + pocRcvdMinusNotSC + (1|subjectIndex), data=mriBehClean, family="binomial", offset=pred);
summary(model2_potc_receivedDiff_type_intxn); #AIC = 7589.2. ns

```


***
#### 2) Neighborhood timescale: Shifts 
##### Summary: Risk-taking increases following a positive shift only and the effect is short-lasting (similar to VIC). Shift does not interact with run size or past outcome.
```{r}
model3_signed_shifts = glmer(choice~0 + shiftDiffsc + (1|subjectIndex), data=mriBehClean, family="binomial", offset=pred);
summary(model3_signed_shifts); # signed shift difference, significant

model3_abs_shift = glmer(choice ~ 0 + shiftDiffscABs + (1|subjectIndex), data=mriBehClean, family="binomial", offset=pred);
summary(model3_abs_shift); # absolute shift difference, ns

model3_pos_neg_shifts = glmer(choice ~ 0 + shiftDiffscPOS + shiftDiffscNEG + (1|subjectIndex), data=mriBehClean, family="binomial", offset=pred);
summary(model3_pos_neg_shifts); # both positive and negative shift difference, only positive significant
m3_coef_posShift = fixef(model3_pos_neg_shifts)[1];

## Plot the effect of positive shift
# scaled shift amounts = 0 to .33 (or 0 to 20 nonscaled)
PgamPosShiftZero = 1/(1+exp(-1*( (m3_coef_posShift*0) ))); # should be .5
PgamPosShiftLarge = 1/(1+exp(-1*( (m3_coef_posShift*.33) )));
# probability of gambling following large positive shift = 0.6518448, a %15.2 increase
PgamPosShiftMedium = 1/(1+exp(-1*( (m3_coef_posShift*.16) )));
# probability of gambling following medium positive shift = 0.5754388, a %7.5 increase


plot(c(PgamPosShiftZero, PgamPosShiftMedium,PgamPosShiftLarge), type="l", lwd=3, col="blue", axes=F, ylab="p(gamble)", xlab="positive shift", main="risk taking as a function of positive shift")
axis(1, labels=c("no shift", "medium", "large"), at=c(1,2,3))
axis(2)



```

#### How far back does shift effect go?
```{r}
# create new positive shift variable (n-1)
newMat = matrix(data=NA,nrow=nrow(mriBehClean), ncol=2);
newMat[,1] <- mriBehClean$shiftDiffscPOS; #take data from columns
newMat[2:nrow(newMat),1] <- newMat[1:(nrow(newMat)-1),1]; # removes first row, shifts everything up
newMat[1,1] <- NaN #put Nan in for first row (first trial for subject 1, bc there is no past trial)
newMat[,2]<-c(0,diff(mriBehClean$subjectIndex)); #put differences between subjectIndex into newvector, 1s show up when subject changes
newMat[newMat[,2]==1,]=NaN; #in newmtx, when diff = 1, replace with NaN, this replaces first trial with nan
mriBehClean$shiftDiffscPOS1 = newMat[,1];# add new vector to mriBehClean

# do the regressions
model3_pos_shift_howfarback = glmer(choice ~ 0 + shiftDiffscPOS + shiftDiffscPOS1 + (1|subjectIndex), data=mriBehClean, family="binomial", offset=pred);
summary(model3_pos_shift_howfarback); #short lasting, only trial directly after a shift

```


#### Does positive shift interact with previous run size or past outcome?
```{r}

# positive shift amount and run size before positive shift
model3_shift_pos_runSize = glmer(choice ~ 0 + shiftDiffscPOS*runSizePOS +(1|subjectIndex), data=mriBehClean, family="binomial", offset=pred);
summary(model3_shift_pos_runSize); # all betas ns


# both positive and negative shift and run size before positive and negative shift
model3_shift_pos_neg_runSize = glmer(choice ~ 0 + shiftDiffscPOS*runSizePOS + shiftDiffscNEG*runSizeNEG + (1|subjectIndex), data=mriBehClean, family="binomial", offset=pred);
summary(model3_shift_pos_neg_runSize); #all betas ns



# Does positive shift interact with past outcome?
model3_posShift_potc_intxn = glmer(choice ~ 0 + shiftDiffscPOS*poc1scaled + (1|subjectIndex), data=mriBehClean, family="binomial", offset=pred);
summary(model3_posShift_potc_intxn); #all betas ns


```

***
#### 3) Global timescale: Cumulative earnings (and trial) 
##### Summary: Cumulative earnings are more tied to trial than previous datasets, even VIC. Earnings and trial have opposite effects with risk-taking increasing with earnings and decreasing across the task. There is a trending interaction between trial and earnings (p=.06). AIC is better in model that includes both terms and an interaction between them.
```{r}

# First looking at earnings and trial in a model (no past outcome, shift variable)
model4_earnings_trial = glmer(choice~0 + earningsNormalized + trialSC + (1|subjectIndex), data=mriBehClean, family="binomial", offset=pred);
summary(model4_earnings_trial); # both significant, betas similar size but opposite valence, AIC = 7657.1 


# pull and store coefficients
m4_coef_trial_Earn = fixef(model4_earnings_trial);
earnCoef = m4_coef_trial_Earn[1];
triCoef = m4_coef_trial_Earn[2];

# plot a couple of subs' earnings and pgamble over the task as a function of earnings and trial
sub1 = mriBehClean[mriBehClean$subjectIndex==7,];
PgamSub1EarnTrial =1/(1+exp(-1*( (triCoef*sub1$trialSC) + (earnCoef*sub1$earningsNormalized) )));

sub2 = mriBehClean[mriBehClean$subjectIndex==35,];
PgamSub2EarnTrial =1/(1+exp(-1*( (triCoef*sub2$trialSC) + (earnCoef*sub2$earningsNormalized) )))

sub3 = mriBehClean[mriBehClean$subjectIndex==52,];
PgamSub3EarnTrial =1/(1+exp(-1*( (triCoef*sub3$trialSC) + (earnCoef*sub3$earningsNormalized) )))

sub4 = mriBehClean[mriBehClean$subjectIndex==15,];
PgamSub4EarnTrial =1/(1+exp(-1*( (triCoef*sub4$trialSC) + (earnCoef*sub4$earningsNormalized) )))

sub5 = mriBehClean[mriBehClean$subjectIndex==28,];
PgamSub5EarnTrial =1/(1+exp(-1*( (triCoef*sub5$trialSC) + (earnCoef*sub5$earningsNormalized) )))

plot(PgamSub1EarnTrial, type="l", col="darkgreen", lwd=3, ylim=c(.4,.6), ylab="p(gamble)", xlab="trial", main="risk taking as a function\n of trial and earnings")
lines(PgamSub2EarnTrial, col="darkred", lwd=3);
lines(PgamSub3EarnTrial, col="darkblue", lwd=3);
lines(PgamSub4EarnTrial, col="darkorange", lwd=3);
lines(PgamSub5EarnTrial, col="goldenrod", lwd=3);
legend("bottomright", legend=c("sub 7","sub 15", "sub 28" ,"sub 35", "sub 52"), lty = 1, lwd=3, bty="n", col=c("darkgreen", "darkorange", "goldenrod", "darkred","darkblue"), cex=.75)

plot(sub1$earningsNormalized,type="l", col="darkgreen", lwd=3, xlab="trial", ylab="earnings (normalized)", main="earnings across the task")
lines(sub2$earningsNormalized, col="darkred", lwd=3)
lines(sub3$earningsNormalized, col="darkblue", lwd=3)
lines(sub4$earningsNormalized, col="darkorange", lwd=3)
lines(sub5$earningsNormalized, col="goldenrod", lwd=3)

legend("bottomright", legend=c("sub 7","sub 15", "sub 28" ,"sub 35", "sub 52"), lty = 1, lwd=3, bty="n", col=c("darkgreen", "darkorange", "goldenrod", "darkred","darkblue"), cex=.75)

# Plot #1 basically shows the difference between earnings and trial

```


```{r}
# Model and plot with interaction term between earnings and trials
    # Interaction was trending here, so I am not sure how much to focus on this. The above model and plots seem more informative.
model4_earnings_trial_intxn = glmer(choice~0 + earningsNormalized*trialSC + (1|subjectIndex), data=mriBehClean, family="binomial", offset=pred);
summary(model4_earnings_trial_intxn); # interaction trending, effects of trial and earnings similar as previous models except that earnings beta is slightly smaller now AIC = 7655.5

```


Plot cumulative earnings for all participants across the task
```{r}
plot(mriBehClean$earnings[mriBehClean$subjectIndex==1], type = "l",lwd = 2, ylim = c(0,max(mriBehClean$earnings)), xlim= c(0,219), main = "Earnings across task\n each line is a participant", ylab = "earnings", xlab="trial number", axes=FALSE)
axis(1, label = c(1, 219), at = c(1,219), tck = 0, lwd = 3)
axis(2, label = c(0, max(mriBehClean$earnings)), at = c(0,max(mriBehClean$earnings)), tck = 0, lwd =3)
for(s in 2:nSub){
  points(mriBehClean$earnings[mriBehClean$subjectIndex==s], type="l", lwd = 1, col = mriBehClean$subjectIndex/.2+s)
};
```



##### Do earnings interact with outcome? 
```{r}
# Earnings interact with past outcome in previous datasets, does that happen here?
model4_earnings_potc_intxn = glmer(choice~0 + earningsNormalized*poc1scaled + trialSC*poc1scaled + (1|subjectIndex), data=mriBehClean, family="binomial", offset=pred);
summary(model4_earnings_potc_intxn); # AIC = 7560.0 
# past outcome negative effect
# interaction between outcomes and earnings are significant. 
# interaction between outcomes and trial are trending at p=.09 
# Main effects of earnings and trial go away (consistent with previous datasets, eg. VIC). 



# store model results
m4_earnPOCintxn_coefs = fixef(model4_earnings_potc_intxn)
earnCoef_2 = m4_earnPOCintxn_coefs[1] 
pocCoef = m4_earnPOCintxn_coefs[2];
pocEarnCoef = m4_earnPOCintxn_coefs[4]
pocTrialCoef = m4_earnPOCintxn_coefs[5]

# PSH did a thing to figure out what the effect of past outcome is given the difference between expectations (trial) and how someone is doing (earnings). Since they are both scaled 0 to 1, you can do the following:
# past outcome beta + (earnings x otc beta * pick an earning value) + (trial x otc beta * pick a beta value)

# earlier in the task:
# pocCoef + pocEarnCoef*.2 + pocTrialCoef*.3 = -1.027033   # doing worse than expected 
# pocCoef + pocEarnCoef*.3 + pocTrialCoef*.3 =  -0.238776  # doing as expected 
# pocCoef + pocEarnCoef*.4 + pocTrialCoef*.3 =  0.5494805  # doing better than expected

# middle of the task
# pocCoef + pocEarnCoef*.5 + pocTrialCoef*.6 = -0.5019535  # doing worse than expected 
# pocCoef + pocEarnCoef*.6 + pocTrialCoef*.6 =  0.2863031  # doing as expected 
# pocCoef + pocEarnCoef*.7 + pocTrialCoef*.6 =  1.07456    # doing better than expected

# late in the task:
# pocCoef + pocEarnCoef*.7 + pocTrialCoef*.8 = -0.1519007  # doing worse than expected 
# pocCoef + pocEarnCoef*.8 + pocTrialCoef*.8 = 0.6363558   # doing as expected 
# pocCoef + pocEarnCoef*.9 + pocTrialCoef*.8 =  1.424612   # doing better than expected

# Overall, when participants did worse than expected, they took less risks and when earnings are more than expected, they took more risks and this pattern is stronger following a large outcome relative to a small outcome. It is possible that past outcome is the vehicle for the interactio between earnings and outcome, and trial and outcome. Likely a discussion for the supplement as a possible "why" for the interaction between two timescales.

# Plot interaction between outcome and earnings

poc= rep(c(0,.5,1), times =3)
earnings = rep(c(.0, .5, 1), each =3)


PgamPOCearningsIntxn =1/(1+exp(-1*( (earnCoef_2*earnings) + (pocCoef*poc) + (pocEarnCoef*poc*earnings) )));

plot(PgamPOCearningsIntxn[1:3], type="l", lwd = 3, col = "pink", ylab= "p(gamble)", xlab="past outcome", axes=F, ylim= c(min(PgamPOCearningsIntxn), max(PgamPOCearningsIntxn)), main="risk taking as a function of \n earnings and past outcome");
lines(PgamPOCearningsIntxn[4:6], lwd=3, col="pink2")
lines(PgamPOCearningsIntxn[7:9], lwd=3, col="pink4")
axis(2)
axis(1, at=c(1:3), labels = c("small", "medium", "large"))
legend("right", legend=c("zero", "medium", "large"), bty="n", lty=1, lwd=3, col=c("pink","pink2", "pink4"), title="earnings:")


# If we add shift to the model above what happens?
# similar pattern in behavior, interaction between outcome and trial is a little weaker (p=.1) and trial and earnings not significant. Strong effect of positive shift AIC =  7552.4 - including shift improves model fit.
model4_earnings_potc_intxn_shift = glmer(choice~0 + earningsNormalized*poc1scaled + trialSC*poc1scaled + shiftDiffscPOS + (1|subjectIndex), data=mriBehClean, family="binomial", offset=pred);
summary(model4_earnings_potc_intxn_shift);
```


### Each timescale in a single model:
#### Summary: Similar effects that we have noted prior: negative past outcome effect that interacts with cumulative earnings and positive shift effect. 
```{r}
model5_potc_posshift_earn_trial = glmer(choice ~ 0 + poc1scaled*earningsNormalized + shiftDiffscPOS + trialSC + (1|subjectIndex), data=mriBehClean, family="binomial", offset=pred)

summary(model5_potc_posshift_earn_trial); # everything significant, AIC = 7553.0 
```

##### Plot earnings x outcome effect using the model above (the interaction term is much smaller than in m4_earning_potc_intxn model), so we'd expect the switching of the past outcome effect to be less intense:
```{r}
# store model results
model5_coef = fixef(model5_potc_posshift_earn_trial)
m5earnCoef = model5_coef[2]; 
m5pocCoef = model5_coef[1];
M5intxnCoef = model5_coef[5];

# Plot interaction between outcome and earnings

poc= rep(c(0,.25,.5,.75, 1), times =5);
earnings = rep(c(0,.25,.5,.75, 1), each =5);


PgamPOCearningsIntxn =1/(1+exp(-1*( (m5earnCoef*earnings) + (m5pocCoef*poc) + (M5intxnCoef*poc*earnings) )));

plot(PgamPOCearningsIntxn[1:5], type="l", lwd = 3, col = "pink", ylab= "p(gamble)", xlab="past outcome ($)", axes=F, ylim= c(0,1), main="risk taking as a function of \n earnings and past outcome (big model 5)");
lines(PgamPOCearningsIntxn[6:10], lwd=3, col="lightpink")
lines(PgamPOCearningsIntxn[11:15], lwd=3, col="pink2")
lines(PgamPOCearningsIntxn[16:20], lwd=3, col="pink3")
lines(PgamPOCearningsIntxn[21:25], lwd=3, col="pink4")
axis(2)
axis(1, at=c(1:5), labels = round(poc[1:5]*max(mriBehClean$riskyGain), digits=2))
legend("bottomleft", legend=c("zero", "small", "medium", "medium-large", "large"), bty="n", lty=1, lwd=3, col=c("pink","lightpink", "pink2" ,"pink3", "pink4"), title="earnings:")
```


```{r} 
# In the figure above showing risk taking as a function of earnings and trial because they have opposite effects. Could it be that these effects are capturing the overall difference between actual earnings and expected earnings (which could be captured by a linear regressor like trial)? This could imply that people are adjusting their risky choice behavior depending on how they are doing compared to how they EXPECT to be doing. If that is the case, then points above p(Gamble) = .5 implies that when people do better than expected, there is more risk-seeking and points below p(Gamble) = .5 implies that when people are doing worse than expected, there is less risk-seeking.

# Our task includes small --> large shifts up and down which could add to how people may expect to be doing (are they adjusting their expectations differently across the levels of context)? One way to account for this is by a 'level-tracking' variable (just adding up level on each trial, which will be a very similar variable to cumulative earnings). This variable is scaled between 0 and 1 for each participant (normalized within participant)


# Run some regressions adding level-tracking and compare to our model above with trial, earnings, poc*earnings, positive shift (AIC = 7553.0).


# trial, level tracking, earnings, poc, positive shift, earnings*poc. 
model4_expectedEarn = glmer(choice~0 + trialSC + earningsNormalized*poc1scaled + levelTrackingNorm + shiftDiffscPOS + (1|subjectIndex), data=mriBehClean, family="binomial", offset=pred);
# AIC = 7554.5
#                              Estimate Std. Error z value Pr(>|z|)    
#trialSC                        -2.4437     0.8837  -2.765  0.00569 ** 
#earningsNormalized              1.3481     1.3463   1.001  0.31666    
#poc1scaled                     -0.7936     0.1696  -4.681 2.86e-06 ***
#levelTrackingNorm               0.9764     1.4523   0.672  0.50139    
#shiftDiffscPOS                  2.4201     0.7479   3.236  0.00121 ** 
#earningsNormalized:poc1scaled   1.8089     0.3328   5.436 5.46e-08 ***

# larger AIC than model without level tracking and effect of earnings goes away and level tracking variable is not significant

# trial, level tracking, level tracking * poc, positive shift (no cumulative earnings).
model4_expectedEarn_noCumulativeEarn = glmer(choice~0 + trialSC + levelTrackingNorm*poc1scaled + levelTrackingNorm + shiftDiffscPOS + (1|subjectIndex), data=mriBehClean, family="binomial", offset=pred);  
# all significant, AIC =  7555.0 which is worse than model with earnings and level tracking (AIC = 7554.5) and model with earnings only (AIC = 7553.0)

# replacing cumulative earnings with level tracking variable  - results resemble the model when using cumulative earnings but model fails to converge. The beta estimates for trial and level tracking are similar but opposite direction and the interaction between poc and level tracking estimate/p value are similar to cumulatve earnings and poc scaled in previous model. Is level tracking and cumulative earnings too similar?

# take out trial 
model4_expectedEarn_noTrial = glmer(choice~0 + earningsNormalized*poc1scaled + levelTrackingNorm + shiftDiffscPOS + (1|subjectIndex), data=mriBehClean, family="binomial", offset=pred);
summary(model4_expectedEarn_noTrial); # AIC = 7560.5 - this has larger AIC than our original model (AIC = 7553.0)


# The best model includes trial and cumulative earnings (not level tracking). This seems like expectations are not changing level-wise. It looks like people are not significantly adjusting their expectations (in Khaw (2017) people are adjusting after hundreds of trials). If it is the case that people are not adjusting their expectations, are they not adjusting their reference point?




```


A few things seem to be happening based on our best model (model5_potc_posshift_earn_trial). 
# 1) There is a negative past outcome effect
# 2) There is a If people's risky choice behavior is reflecting the difference between how they are doing and how they EXPECT to be doing.
```{r}
#                               Estimate Std. Error z value Pr(>|z|)    
# poc1scaled                     -0.7851     0.1691  -4.644 3.42e-06 ***
# earningsNormalized              2.0781     0.8126   2.557  0.01055 *  
# shiftDiffscPOS                  2.4082     0.7488   3.216  0.00130 ** 
# trialSC                        -2.1953     0.8022  -2.737  0.00621 ** 
# poc1scaled:earningsNormali zed   1.7987     0.3325   5.410 6.31e-08 ***
# AIC = 7553 (model5_potc_posshift_earn_trial)

# Add and interaction between trial and poc

model5_potc_posshift_earn_trial_intxns = glmer(choice~0 + earningsNormalized*poc1scaled + trialSC*poc1scaled + shiftDiffscPOS + (1|subjectIndex), data=mriBehClean, family="binomial", offset=pred);
summary(model5_potc_posshift_earn_trial_intxns); # AIC =  7552.4 - slightly better AIC than model above

#                               Estimate Std. Error z value Pr(>|z|)    
# earningsNormalized              0.6839     1.1742   0.582   0.5603    
# poc1scaled                     -0.7891     0.1689  -4.671    3e-06 ***
# trialSC                        -0.8086     1.1637  -0.695   0.4871    
# shiftDiffscPOS                  2.3355     0.7484   3.121   0.0018 ** 
# earningsNormalized:poc1scaled   7.3235     3.4204   2.141   0.0323 *  
# poc1scaled:trialSC             -5.4923     3.3842  -1.623   0.1046  

# The interaction between past outcome and trial is trending p=.1. Past outcome, shift, and interaction between past outcome and earnings still there. Now the main effect of earnings and trial not there.

```







#### Individual-level analyses (glm)
###### output = pocResults {subID, beta, pval}


```{r}
subsTriLevMods = list();
subsPocMods = list();
trialLevelResults = as.data.frame(matrix(data = NA, nrow = nSub, ncol=3, dimnames=list(c(NULL), c("subID","beta","pval"))))
pocResults = as.data.frame(matrix(data = NA, nrow = nSub, ncol=3, dimnames=list(c(NULL), c("subID","beta","pval"))))

for (s in 1:nSub) {
  sub = mriBehClean[mriBehClean$subjectIndex==subIDs[s],]; # pull out a single subject
  
  subsTriLevMods[[s]] = glm(choice~gainSC + altSC + grndEVscaled, data=sub, family="binomial"); # run the trial levelm odel

  sub$pred = predict(subsTriLevMods[[s]],type='link'); # get predicted values
  
  subsPocMods[[s]] = glm(choice~poc1scaled, data=sub, family="binomial", offset=pred); # past outcome model with predicted values
  
  tmp =summary(subsPocMods[[s]]); #store coefficients from poc model
  pocResults$subID[s] = subIDs[s]; # fill in sub ID
  pocResults$beta[s] = tmp$coefficients[[2]]; # store beta
  pocResults$pval[s] = tmp$coefficients[[8]]; # store pvalue
}; 


print(pocResults)
```

**Plot the individual past outcome results**
```{r}

plot(pocResults$beta, ylim=c(min(pocResults$beta),max(pocResults$beta)), pch=16, main=sprintf("Individual past outcome estimates (n=%s)", nSub), xlab="participant", ylab="estimate", col= ifelse(pocResults[,3]<.05, "green", ifelse(pocResults[,3]<.1 & pocResults$pval>.05,"blue", "black")), cex=1.75); # blue is trending, green is significant, black is neither
abline(a=0,b=0, col="grey");
legend("topright", legend= c("p < .05", ".05 < p < .1", "p > .1"), bty="n", pch = 16, col=c("green", "blue", "black"));
```

