---
title: "createEventFiles"
author: "Hayley Brooks"
date: "5/27/2021"
output: html_document
---
##### Output:
  - An onset/timing file for each event on each run (3) for every participant (51)
  - events we are modeling for now: choice option display, decision, outcome, modulated by monetary amounts

##### Timing information
-Choice options were displayed for 2 seconds (forced viewing) then participants had 2 seconds to respond. Once they responded, the ISI (varied 1.75s-5.75s) began and anytime remaining in the 2 second response window was added to the ITI at the end of the trial. After the ISI, the outcome was shown for 1 second followed by the ITI (varied .75 - 4.75 plus the leftover response time (2-RT) ). ITI, ISI and RT are included in the raw dataset loaded below.

- There was a 15 second fixation at the start of each block (to allow the scanner to settle). The first trial started immediately after the fixation ended.


#### Set up
```{r}
rm(list=ls());  # clear environment


library("config");
config <- config::get();

# load timing files:
eventFilePath = file.path(config$path$data$event_files); # location of event files for each participant and each run
eventFiles = list.files(eventFilePath, pattern= "*_event.csv", full.names = T); # store names of files that we will need

# load raw dataset for choiceset
RDMgroupCSVpath = file.path(config$path$data$raw_group,config$csvs$RDM_group_raw_csv);
RDMraw = read.csv(RDMgroupCSVpath); 

# Remove participant 13 (did not start risky decision-making task)
RDMraw = RDMraw[RDMraw$subjectIndex!=13,]
```

#### Subject Information
```{r}
subNum = unique(RDMraw$subjectIndex);
nSubRaw = length(subNum); # should be 51

# Create a vector that has the sub IDs formatted as in BIDS (e.g. 001, 002)
subID_bids = vector(); # create empty vector

for (s in 1: nSubRaw){
  if(s<10){
   subID_bids[s]=paste("00",subNum[s],sep="")
  }
  else {
   subID_bids[s]=paste("0", subNum[s],sep="")
  }
};



```

#### Create txt files
For a given trial, there are 5 events: choice display, choice/RT, ISI, outcome, ITI and 73 trials in each run for a total of 365 events in a run (1095 total events across all three runs because 5 x 219 = 1095);

We had a 15 second delay which = 32.6087 TRs, so we will delete 32 volumes in FSL and will need to adjust the timing files by .6087 seconds. From FSL: "remember when setting up the design matrix that the timings in the design matrix start at t=0 seconds, and this corresponds to the start of the first image taken after the deleted scans. In other words, the design matrix starts after the deleted scans have been deleted.""

To create the onset files for FSL, we use timing information from the sub_0##_run#_event.csv files which were created using the timing output from the study sessions. We will start each trial with stimulus start (not trial start) because there is a very slight delay between trial start and stimulus start (trial starts, computer randomly decides location of gamble/safe location on screen, then shows the stimuli)

We will be combining duration for stimulus and decision window because these are identical with the exception that participants were allowed to respond once the decision window started.

For modeling decision(action), it would be when RT happened in the time series (not RTs themselves)

When done, add these timing files to RDAC







#### Create onset files for CHOICE DISPLAY

- choiceDisp_meanEV_run#.txt: choice display modulated by mean expected value
- choiceDisp_gainAmt_run#.txt: choice display modulated by gain amount (mean center?)
- choiceDisp_safeAmt_run#.txt: choice display modulated by safe amount (mean center?)


```{r} 

# Onset file names (will dynamically add run number once files are created)
#outcomeOnsetFileNames = c("outcomeDisp_otcAmt_run","outcomeDisp_otcWinAmt_run", "outcomeDisp_otcLossAmt_run", "outcomeDisp_otcSafeAmt_run");
#decisionOnsetFileNames = c("decision_run", "decisionGamble_run", "decisionSafe_run");

# each participant has three event files, one for each run
# each event file has 438 rows (73 trials x 6 events)
nTblock = 73;
nEvents = 6;
nRun = 3;
offset = .6087;

for (s in 1:nSubRaw) {
  
  ind = grep(sprintf("sub-%s_run",subID_bids[s]), eventFiles); # get indices of event files for participant 
  RDMsub = RDMraw[RDMraw$subjectIndex==subNum[s],]; # load risky decision-making data
   
  for (r in 1:nRun){
    
    eventrun = read.csv(eventFiles[ind[r]]); # load file for one run
    
   
    ###   CHOICE DISPLAY ###
    stimStartInd = which(eventrun$eventType=="stimulusStart");  # index start of stimulus display
    decWindowInd = which(eventrun$eventType=="decisionWindow"); # index start of decision window
   
    # store events by onset, duration and modulation (mean ev, gain, safe)
    onset = eventrun$onset[stimStartInd]; # onset is stimStart onset
    duration = eventrun$duration[stimStartInd] + eventrun$duration[decWindowInd]; # duration is stimStart duration + decisionWindow duration
    modulationEV = RDMsub$meanEV[RDMsub$block==r]; # mean EV
    modulationGain = RDMsub$riskyGain[RDMsub$block==r]; # risky gain amount
    modulationSafe = RDMsub$alternative[RDMsub$block==r]; # risky safe amount
    
    
    # Offset the onset times by .6087s (see notes above)
    onset = onset + offset;
    
    
    # store onset, duration and modulation into a single data frame
    choiceMeanEV = cbind(onset, duration, modulationEV);
    choiceGain = cbind(onset, duration, modulationGain);
    choiceSafe = cbind(onset, duration, modulationSafe);
    
    # create file names
    choiceMEVfileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("choiceDisp_meanEV_run",r,sep=""));
    choiceGAINfileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("choiceDisp_gainAmt_run",r,sep=""));
    choiceSAFEfileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("choiceDisp_safeAmt_run",r,sep=""));
    
    # save files
    write.table(choiceMeanEV, file=choiceMEVfileName, row.names = F, col.names = F, sep="\t");
    write.table(choiceGain, file=choiceGAINfileName, row.names = F, col.names = F, sep="\t");
    write.table(choiceSafe, file=choiceSAFEfileName, row.names = F, col.names = F, sep="\t");

    
  } # end for (r in 1:nRun)
} # end for (s in 1:nSubRaw)

```
  
  
  
#### Create onset files for OUTCOME
- outcomeDisp_otcAmt_run#.txt: all outcomes, outcome amount
- outcomeDisp_otcWinAmt_run#.txt: win, received - not received 
- outcomeDisp_otcLossAmt_run#.txt: loss, received - not received
- outcomeDisp_otcSafeAmt_run#.txt: safe, amount received 

```{r}



# each participant has three event files, one for each run
# each event file has 438 rows (73 trials x 6 events)
nTblock = 73;
nEvents = 6;
nRun = 3;
offset = .6087;

for (s in 1:nSubRaw) {
  
  ind = grep(sprintf("sub-%s_run",subID_bids[s]), eventFiles); # get indices of event files for participant 
  RDMsub = RDMraw[RDMraw$subjectIndex==subNum[s],]; # load risky decision-making data
   
  for (r in 1:nRun){
    
    eventrun = read.csv(eventFiles[ind[r]]); # load file for one run
    
   
    ###   OUTCOME    ###
    
    outcomeInd = which(eventrun$eventType=="outcome");  # index start of outcome display for all outcomes
    gainOutcomeTrial = RDMsub$triBlock[RDMsub$outcome==RDMsub$riskyGain & RDMsub$block==r];   # RDM trial number of gain outcome for block r
    lossOutcomeTrial = RDMsub$triBlock[RDMsub$outcome==RDMsub$riskyLoss & RDMsub$block==r];   # RDM trial number of loss outcome for block r
    safeOutcomeTrial = RDMsub$triBlock[RDMsub$outcome==RDMsub$alternative & RDMsub$block==r]; # RDM trial number of safe outcome for block r
    
    # Store events by onset, duration and modulation (this looks a little different for each outcome onset file)
      # all outcomes
        onsetAllotc = eventrun$onset[outcomeInd]; # onset is outcome onset
        durationAllotc = eventrun$duration[outcomeInd]; # duration is outcome duration
        modulationAllotc = RDMsub$outcome[RDMsub$block==r]; # outcome amount

      # gain outcomes
        onsetGainotc = onsetAllotc[gainOutcomeTrial]; 
        durationGainotc = durationAllotc[gainOutcomeTrial]; 
        modulationGainotc = modulationAllotc[gainOutcomeTrial]
          
      # loss outcomes
        onsetLossotc = onsetAllotc[lossOutcomeTrial]; 
        durationLossotc = durationAllotc[lossOutcomeTrial]; 
        modulationLossotc = modulationAllotc[lossOutcomeTrial]
        
      # safe outcomes
        onsetSafeotc = onsetAllotc[safeOutcomeTrial]; 
        durationSafeotc = durationAllotc[safeOutcomeTrial]; 
        modulationSafeotc = modulationAllotc[safeOutcomeTrial]
          
          
    # Offset the onset times by .6087s (see notes above)
    onsetAllotc = onsetAllotc + offset;
    onsetGainotc = onsetGainotc + offset;
    onsetLossotc = onsetLossotc + offset;
    onsetSafeotc = onsetSafeotc + offset;
    
    # store onset, duration and modulation into a single data frame
    outcomeAmt = cbind(onsetAllotc, durationAllotc, modulationAllotc);
    GAINoutcomeAmt = cbind(onsetGainotc, durationGainotc, modulationGainotc);
    LOSSoutcomeAmt = cbind(onsetLossotc, durationLossotc, modulationLossotc);
    SAFEoutcomeAmt = cbind(onsetSafeotc, durationSafeotc, modulationSafeotc);
    
    
    # create file names
    outcomeAmtfileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("outcomeDisp_otcAmt_run",r,sep=""));
    GAINoutcomeAmtfileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("outcomeDisp_otcWinAmt_run",r,sep=""));
    LOSSoutcomeAmtfileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("outcomeDisp_otcLossAmt_run",r,sep=""));
    SAFEoutcomeAmtfileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("outcomeDisp_otcSafeAmt_run",r,sep=""));

    # save files
    write.table(outcomeAmt, file=outcomeAmtfileName, row.names = F, col.names = F, sep="\t");
    write.table(GAINoutcomeAmt, file=GAINoutcomeAmtfileName, row.names = F, col.names = F, sep="\t");
    write.table(LOSSoutcomeAmt, file=LOSSoutcomeAmtfileName, row.names = F, col.names = F, sep="\t");
    write.table(SAFEoutcomeAmt, file=SAFEoutcomeAmtfileName, row.names = F, col.names = F, sep="\t");

    
  } # end for (r in 1:nRun)
} # end for (s in 1:nSubRaw)

```

#### Create onset files for DECISION -  
- decision_run#.txt: choice (generally)
- decisionGamble_run#.txt: chose gamble
- decisionSafe_run#.txt: choice safe

- create files that modulate decision by mean ev, risky gain and safe amounts


- ***big thing here is how to incorporate reaction time and does the timing add up between the event files (when the decision window ends) and reaction time in the choice set dataframe. For the decision time series, the onset of the choice will be the onset of the decision window + reaction time. The duration will be 0 seconds.

```{r}

# each participant has three event files, one for each run
# each event file has 438 rows (73 trials x 6 events)
nTblock = 73;
nEvents = 6;
nRun = 3;
offset = .6087;

for (s in 1:nSubRaw) {
  
  ind = grep(sprintf("sub-%s_run",subID_bids[s]), eventFiles); # get indices of event files for participant 
  RDMsub = RDMraw[RDMraw$subjectIndex==subNum[s],]; # load risky decision-making data
   
  for (r in 1:nRun){
    
    eventrun = read.csv(eventFiles[ind[r]]); # load file for one run
    
    ###   DECISION/RT    ###
  
    decisionInd = which(eventrun$eventType=="decisionWindow");  # index start of decision window
    gambleTrial = RDMsub$triBlock[RDMsub$choice==1 & RDMsub$block==r];   # RDM trial number of gamble choice for block r
    safeTrial = RDMsub$triBlock[RDMsub$choice==0 & RDMsub$block==r]; # RDM trial number of safe choice for block r    
    
    
    
    # Store events by onset, duration and modulation (this looks a little different for each outcome onset file)
      # all decision types
        onsetAllDecision = eventrun$onset[decisionInd] + RDMsub$RTs[RDMsub$block==r]; # onset is decision window onset + RTs
        durationAllDecision = 0; # duration of decision will be 0
        modulationEV = RDMsub$meanEV[RDMsub$block==r]; # mean EV
        modulationGain = RDMsub$riskyGain[RDMsub$block==r]; # risky gain amount
        modulationSafe = RDMsub$alternative[RDMsub$block==r]; # risky safe amount
            
      # gamble decision trials
        onsetGambleDecision = onsetAllDecision[gambleTrial]; 
        durationGambleDecision = 0; 
        modulateGambleGain = modulationGain[gambleTrial]
        modulateGambleSafe = modulationSafe[gambleTrial]
        modulateGambleEV = modulationEV[gambleTrial]
        

      # safe decision trials
        onsetSafeDecision = onsetAllDecision[safeTrial]; 
        durationSafeDecision = 0; 
        modulateSafeGain = modulationGain[safeTrial]
        modulateSafeSafe = modulationSafe[safeTrial]
        modulateSafeEV = modulationEV[safeTrial]
        
        
    # Offset the onset times by .6087s (see notes above)
      onsetAllDecision = onsetAllDecision + offset
      onsetGambleDecision = onsetGambleDecision + offset
      onsetSafeDecision = onsetSafeDecision + offset
    
    # store onset, duration and modulation into a single data frame
      EVdecisionAll   = cbind(onsetAllDecision, durationAllDecision, modulationEV);
      GAINdecisionAll = cbind(onsetAllDecision, durationAllDecision, modulationGain);
      SAFEdecisionAll = cbind(onsetAllDecision, durationAllDecision, modulationSafe);
      
      EVdecisionGamble =   cbind(onsetGambleDecision, durationGambleDecision, modulateGambleEV);
      GAINdecisionGamble = cbind(onsetGambleDecision, durationGambleDecision, modulateGambleGain);
      SAFEdecisionGamble = cbind(onsetGambleDecision, durationGambleDecision, modulateGambleSafe);
      
      EVdecisionSafe =  cbind(onsetSafeDecision, durationSafeDecision, modulateSafeEV);
      GAINdecisionSafe = cbind(onsetSafeDecision, durationSafeDecision, modulateSafeGain); 
      SAFEdecisionSafe = cbind(onsetSafeDecision, durationSafeDecision, modulateSafeSafe);
    
    # create file names
    
    # create file names
    decisionAllmeanEVfileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("decisionAll_meanEVamt_run",r,sep=""));
    decisionAllGainfileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("decisionAll_gainAmt_run",r,sep=""));
    decisionAllSafefileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("decisionAll_safeAmt_run",r,sep=""));  
      
    decisionGamblemeanEVfileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("decisionGamble_meanEVamt_run",r,sep=""));
    decisionGambleGainfileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("decisionGamble_gainAmt_run",r,sep=""));
    decisionGambleSafefileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("decisionGamble_safeAmt_run",r,sep="")); 
      
    decisionSafemeanEVfileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("decisionSafe_meanEVamt_run",r,sep=""));
    decisionSafeGainfileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("decisionSafe_gainAmt_run",r,sep=""));
    decisionSafeSafefileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("decisionSafe_safeAmt_run",r,sep=""));
      
      
    # save files
    write.table(EVdecisionAll, file=decisionAllmeanEVfileName, row.names = F, col.names = F, sep="\t");
    write.table(GAINdecisionAll, file=decisionAllGainfileName, row.names = F, col.names = F, sep="\t");
    write.table(SAFEdecisionAll, file=decisionAllSafefileName, row.names = F, col.names = F, sep="\t");
    
    write.table(EVdecisionGamble, file=decisionGamblemeanEVfileName, row.names = F, col.names = F, sep="\t");
    write.table(GAINdecisionGamble, file=decisionGambleGainfileName, row.names = F, col.names = F, sep="\t");
    write.table(SAFEdecisionGamble, file=decisionGambleSafefileName, row.names = F, col.names = F, sep="\t");
      
    write.table(EVdecisionSafe, file=decisionSafemeanEVfileName, row.names = F, col.names = F, sep="\t");
    write.table(GAINdecisionSafe, file=decisionSafeGainfileName, row.names = F, col.names = F, sep="\t");
    write.table(SAFEdecisionSafe, file=decisionSafeSafefileName, row.names = F, col.names = F, sep="\t");

    
  } # end for (r in 1:nRun)
} # end for (s in 1:nSubRaw)

```

Create files for missed trials - we want to do this uniformly across timing file types above
Each row either has a 1 (don't include this trial - its 'missing') or 0 (keep this trial)

```{r}

nTblock = 73;
nRun = 3;

for (s in 1:nSubRaw) {  
  
  missedTrialsRun1 = matrix(data=0, nrow = nTblock, ncol=1); # all zeroes
  missedTrialsRun2 = matrix(data=0, nrow = nTblock, ncol=1); # all zeroes
  missedTrialsRun3 = matrix(data=0, nrow = nTblock, ncol=1);
    #vector(mode="numeric", length = nTblock); # all zeroes
  
  RDMsub = RDMraw[RDMraw$subjectIndex==subNum[s],]; # load risky decision-making data
  
    # pull out each run  
      run1 = RDMsub[RDMsub$block==1,]; 
      run2 = RDMsub[RDMsub$block==2,]; 
      run3 = RDMsub[RDMsub$block==3,]; 
    
    # index the missed trials
      missTrun1ind = which(is.na(run1$choice)); 
      missTrun2ind = which(is.na(run2$choice)); 
      missTrun3ind = which(is.na(run3$choice)); 
  
    # change missed trials to 1 in our complementary dummy EV files (as FSL calls it)
      missedTrialsRun1[missTrun1ind] =1
      missedTrialsRun2[missTrun2ind] =1
      missedTrialsRun3[missTrun3ind] =1
 
    # create files names and save vectors as txt files
          
    missTrun1fileName = sprintf("%s/sub-%s/%s.txt", config$path$data$missedTrials_files,subID_bids[s],"missedTrials_run1");
    missTrun2fileName = sprintf("%s/sub-%s/%s.txt", config$path$data$missedTrials_files,subID_bids[s],"missedTrials_run2");
    missTrun3fileName = sprintf("%s/sub-%s/%s.txt", config$path$data$missedTrials_files,subID_bids[s],"missedTrials_run3");
    
    write.table(missedTrialsRun1, file=missTrun1fileName, row.names = F, col.names = F, sep="\t");
    write.table(missedTrialsRun2, file=missTrun2fileName, row.names = F, col.names = F, sep="\t");
    write.table(missedTrialsRun3, file=missTrun3fileName, row.names = F, col.names = F, sep="\t");
    
      
} # end for (s in 1:nSubRaw)



```


THEN: add notes to the preprocessing about this script, what it does, and its output
THEN: add timing files to RDAC for analysis!
