---
title: "createEventFiles"
author: "Hayley Brooks"
date: "5/27/2021"
output: html_document
---
##### Output:
  - An onset/timing file for each event on each run (3) for every participant (51)
  - events we are modeling for now: choice option display, decision, outcome, modulated by monetary amounts

##### Timing information
-Choice options were displayed for 2 seconds (forced viewing) then participants had 2 seconds to respond. Once they responded, the ISI (varied 1.75s-5.75s) began and anytime remaining in the 2 second response window was added to the ITI at the end of the trial. After the ISI, the outcome was shown for 1 second followed by the ITI (varied .75 - 4.75 plus the leftover response time (2-RT) ). ITI, ISI and RT are included in the raw dataset loaded below.

- There was a 15 second fixation at the start of each block (to allow the scanner to settle). The first trial started immediately after the fixation ended.

- parametric modulations are mean-centered for each functional run for each participant


#### Set up
```{r}
rm(list=ls());  # clear environment


library("config");
config <- config::get();

# load timing files:
eventFilePath = file.path(config$path$data$event_files); # location of event files for each participant and each run
eventFiles = list.files(eventFilePath, pattern= "*_event.csv", full.names = T); # store names of files that we will need

# load raw dataset for choiceset
RDMgroupCSVpath = file.path(config$path$data$raw_group,config$csvs$RDM_group_raw_csv);
RDMraw = read.csv(RDMgroupCSVpath); 

# remove participants we excluded
excludeSub = c(13,16,42,43)
RDMraw = RDMraw[!RDMraw$subjectIndex %in% excludeSub,]

```

#### Subject Information
```{r}
subNum = unique(RDMraw$subjectIndex);
nSubRaw = length(subNum); # should be 51

# Create a vector that has the sub IDs formatted as in BIDS (e.g. 001, 002)
subID_bids = vector(); # create empty vector

for (s in 1: nSubRaw){
  if(s<10){
   subID_bids[s]=paste("00",subNum[s],sep="")
  }
  else {
   subID_bids[s]=paste("0", subNum[s],sep="")
  }
};



```

#### Create txt files
For a given trial, there are 5 events: choice display, choice/RT, ISI, outcome, ITI and 73 trials in each run for a total of 365 events in a run (1095 total events across all three runs because 5 x 219 = 1095);

We had a 15 second delay which = 32.6087 TRs, so we will delete 32 volumes in FSL and will need to adjust the timing files by .6087 seconds. From FSL: "remember when setting up the design matrix that the timings in the design matrix start at t=0 seconds, and this corresponds to the start of the first image taken after the deleted scans. In other words, the design matrix starts after the deleted scans have been deleted."

To create the onset files for FSL, we use timing information from the sub_0##_run#_event.csv files which were created using the timing output from the study sessions. We will start each trial with stimulus start (not trial start) because there is a very slight delay between trial start and stimulus start (trial starts, computer randomly decides location of gamble/safe location on screen, then shows the stimuli)

We will be combining duration for stimulus and decision window because these are identical with the exception that participants were allowed to respond once the decision window started.

For modeling decision(action), it would be when RT happened in the time series (not RTs themselves)

When done, add these timing files to RDAC.


#### Create onset files for CHOICE DISPLAY

- choiceDispMeanEV_run#.txt: choice display modulated by mean expected value (mean centered within runs)
- choiceDispEVGAmt_run#.txt: choice display modulated by ev gain amount (mean center within runs)
- choiceDispSafeAmt_run#.txt: choice display modulated by ev safe amount (mean center within runs)
- choiceDispChosenUnchosen_run#.txt: choice display modulated by chosen-unchosen (mean centered within runs)
- choiceDispNoModulation_run#.txt: choice display with no modulation 
- choiceDispShift_run#.txt: includes trials where shift occurred accounted for at choice display
- choiceDispShiftAmt_run#.txt: includes trials where shift occurred modulated by shift amount (NOT mean centered because they are mean-centered naturally and mean centering within runs creates issue with timing files that FSL doesn't like, scaled)
- choiceDispPastOCAmt_run#.txt: choice display modulated by past outcome amount (mean centered within runs)
- choiceDispEarnExpAmt_run#.txt: choice display modulated by earnings - expectations (using beta weights from behavior; mean-centered across runs)
- choiceDispLinear_run#.txt: choice display modulated by a linear term (0 to 1 over the task; mean-centered across runs)

```{r choice-display} 

# Onset file names (will dynamically add run number once files are created)
#outcomeOnsetFileNames = c("outcomeDisp_otcAmt_run","outcomeDisp_otcWinAmt_run", "outcomeDisp_otcLossAmt_run", "outcomeDisp_otcSafeAmt_run");
#decisionOnsetFileNames = c("decision_run", "decisionGamble_run", "decisionSafe_run");

# each participant has three event files, one for each run
# each event file has 438 rows (73 trials x 6 events)
nTblock = 73;
nEvents = 6;
nRun = 3;
offset = .6087;
scaleby = max(RDMraw$riskyGain, na.rm=T);

# create a choice variable that is coded -1 and 1 (will need this for relative choice (ie. chosen-unchosen))
RDMraw$choiceRecode = RDMraw$choice
RDMraw$choiceRecode[RDMraw$choiceRecode==0] = -1

# create shift variables
RDMraw$shiftDiff = c(0,diff(RDMraw$groundEV)); #difference in ground EV will get the accurate shift amount = -20 to +20
RDMraw$shiftDiff[RDMraw$trial==1]=0 # first trial is always 0
RDMraw$positiveShift = RDMraw$shiftDiff
RDMraw$positiveShift[RDMraw$shiftDiff<0]=0
RDMraw$positiveShiftSC = RDMraw$positiveShift/scaleby

# create past outcome variables
newMat = matrix(data=NA,nrow=nrow(RDMraw), ncol=2)
newMat[,1] <- RDMraw$outcome; #take data from columns
newMat[2:nrow(newMat),1] <- newMat[1:(nrow(newMat)-1),1]; # removes first row, shifts everything up
newMat[1,1] <- NaN #put Nan in for first row (first trial for subject 1, bc there is no past trial)
newMat[,2]<-c(0,diff(RDMraw$subjectIndex)); #put differences between NewSubjectIndex into newvector, 1s show up when subject changes
newMat[newMat[,2]==1,]=NaN; #in newmtx, when diff = 1, replace with NaN, this replaces first trial with nan
RDMraw$poc1 = newMat[,1];# add new vector to RDMraw


# create earnings and expectation variables
# earnings are 0 to 1 across the entire task (not within runs or starting over at the beginning of each run) but are scaled across individuals (not everyone ends at 1)
# expectations are scaled across individuals (i.e. by the single largest cumulative earnings)
# EARNINGS BETA = 2.3959
earningsBeta = 2.3959
# EXPECTATIONS BETA = -2.1927
expectationsBeta = -2.1927
# from model: model5_potc_posshift_earn_trial 


expectations = vector();
earnings=vector(); 
earningsTrialT = vector();
earningsScaledBySub = vector();

subIDs = unique(RDMraw$subjectIndex)
nSub = length(subIDs)

for (s in 1:nSub) {
  sub = RDMraw[RDMraw$subjectIndex==subIDs[s],]
  earningsSubTrialT = vector(); # reset earnings vector for each participant
  earningsSub = vector(); 
  expScaled = vector(); # reset trial vector for each participant
  earningsSubScaled = vector(); # reset scaled earnings vector for each participant
  
  # cumsum function can't handle nans, so create a temp variable where the NaNs are 0s
  tmpOutcomeVec = sub$outcome
  tmpOutcomeVec[is.na(tmpOutcomeVec)]=0
  
  earningsSubTrialT = cumsum(tmpOutcomeVec); # this creates a variable where outcome on a given trial is reflected in the earnings including outcome on the same trial. we will use this variable for when we want to test WHEN earnings are updating, for example, at outcome display
  earningsSub = c(0,earningsSubTrialT[1:length(earningsSubTrialT)-1]); # add zero for first trial and get rid of last trial earnings. This variable includes earnings up until trial t (so only including earnings from previous trial and earlier). this is the variable we use in our behavioral analysis and will be used for modulations during choice display (i.e. before participants gets another outcome and updates earnings).
  expScaled = sub$trial/max(sub$trial)
  
  earningsSubScaled = earningsSub/max(earningsSub) # this normalizes earnings within each participant
  
  earnings = c(earnings,earningsSub); # all earning prior to trial t
  earningsTrialT = c(earningsTrialT, earningsSubTrialT); # all earnings including trial t
  expectations = c(expectations,expScaled);
  earningsScaledBySub = c(earningsScaledBySub,earningsSubScaled)
  
}

RDMraw$expectations = expectations # store linear expectation (scaled)
RDMraw$earnings = earnings; #store earnings 
RDMraw$earningsSC = RDMraw$earnings/max(RDMraw$earnings); #create scaled earnings variable and store it
RDMraw$earningsNormalized = earningsScaledBySub # store normalized earnings 
RDMraw$earningsTrialT = earningsTrialT/max(earningsTrialT) # store earnings that include current trial outcome

RDMraw$relativeEarnings = (earningsBeta*RDMraw$earningsSC) + (expectationsBeta*RDMraw$expectations); # using addition because expectations are negative
# using earnings up until trial t for relative earnings

for (s in 1:nSubRaw) {
#for (s in 1) {  
  ind = grep(sprintf("sub-%s_run",subID_bids[s]), eventFiles); # get indices of event files for participant 
  RDMsub = RDMraw[RDMraw$subjectIndex==subNum[s],]; # load risky decision-making data
   
  
  
  for (r in 1:nRun){
  #for (r in 1){
    RDMsubRun = RDMsub[RDMsub$block==r,] # just get sub RDM data for this run
    eventrun = read.csv(eventFiles[ind[r]]); # load  event file for one run
    

    ###   CHOICE DISPLAY ###
    stimStartInd = which(eventrun$eventType=="stimulusStart");  # index start of stimulus display
    decWindowInd = which(eventrun$eventType=="decisionWindow"); # index start of decision window
    
    # set up onset and duration variables (still include missed trials at this point)
    choiceDispOnset = eventrun$onset[stimStartInd]
    choiceDispDuration = eventrun$duration[stimStartInd] + eventrun$duration[decWindowInd]; # duration is stimStart duration + decisionWindow duration (which is basically RT)
    
    # add onset and duration to RDM data for a given run
    RDMsubRun$choiceDispOnset = choiceDispOnset
    RDMsubRun$choiceDispDuration = choiceDispDuration
    
    #remove missed trials (for these timing files we are only accounting for choice display when choice was made - missed trials are accounted for down below in missed trial timing files)
    missedTrials = RDMsubRun$triBlock[is.na(RDMsubRun$choice)]; # index the missed trials for this run
    if(length(missedTrials>0)){
      RDMsubRun =RDMsubRun[-c(missedTrials),] # remove missed trials
    }


    # store events by onset, duration and modulation (mean ev, gain, safe) and mean center them (by functional run)
    modulationEV = RDMsubRun$meanEV- mean(RDMsubRun$meanEV); # mean EV mean centered within run
    modulationEVG = (RDMsubRun$riskyGain*.5)-mean(RDMsubRun$riskyGain*.5); # ev gamble mean centered within run
    modulationSafe = RDMsubRun$alternative-mean(RDMsubRun$alternative); # safe amount mean centered within run
    modulationRelEarnings = RDMsubRun$relativeEarnings - mean(RDMsub$relativeEarnings) # relative earnings mean centered ACROSS runs
    modulationLinear = RDMsubRun$expectations - mean(RDMsub$expectations) # linear term (0ish to 1 across the task) mean centered ACROSS runs
    
    # create modulation for chosen vs unchosen
    # chosen = 1 * EVG-EVS (so this is trials where choice = 1 and the EV diff on those trials)
    # unchosen = -1 * EVG-EVs
    meanEVDiff = mean((RDMsubRun$riskyGain*.5) - RDMsubRun$alternative)
    modulationChoseUnchosen = RDMsubRun$choiceRecode*((RDMsubRun$riskyGain*.5) - RDMsubRun$alternative)
    modulationChoseUnchosen = modulationChoseUnchosen - meanEVDiff


   # round and scale modulators
    modulationEV = round(modulationEV/scaleby, digits =2);
    #modulationGain = round(modulationGain/scaleby, digits =2);
    modulationEVG = round(modulationEVG/scaleby, digits =2);
    modulationSafe = round(modulationSafe/scaleby, digits =2);
    modulationChoseUnchosen = round(modulationChoseUnchosen/scaleby, digits = 2);
    #modulationRelEarnings = round(modulationRelEarnings/scaleby, digits = 2); earnings are already scaled and doing this make the values super super small. same for earningsTrialT
    
    
    # setting up shift and outcome timing files is a little different from above - 
    # we want to look at these AT the time of  choice display but we just want the trials were a positive shift and where there is a previous outcome
    
    onsetShift = RDMsubRun$choiceDispOnset[RDMsubRun$positiveShiftSC>0] # subset onset when shift occurred
    durationShift = RDMsubRun$choiceDispDuration[RDMsubRun$positiveShiftSC>0] # subset duration when shift occurred
    modulationShift = RDMsubRun$positiveShiftSC[RDMsubRun$positiveShiftSC>0] 
    modulationShift = round(modulationShift, digits=2) # round to 2 decimals (this variable is already scaled)
    
    onsetPOC = RDMsubRun$choiceDispOnset[is.finite(RDMsubRun$poc1)] # subset onset where there was a past outcome
    durationPOC = RDMsubRun$choiceDispDuration[is.finite(RDMsubRun$poc1)] # subset duration where there was a past outcome
    meanPOCAmt = mean(RDMsubRun$poc1[is.finite(RDMsubRun$poc1)]) # calculate mean poc
    modulationPOC = RDMsubRun$poc1[is.finite(RDMsubRun$poc1)] - meanPOCAmt # mean center the modulator
    modulationPOC = round(modulationPOC/scaleby, digits = 2); # scale and round to 2 decimals
    # note: for the past outcome timing files, we are not including trials where there was not a past outcome (this is always the first trial in run 1 and any trials following a missed choice). These NAN past outcomes are accounted for by other timing files where other things were happening so we don't treat the non-poc trials as missed trials like we do actual missed trials.
    
    # Offset the onset times by .6087s (see notes above)
    onset = RDMsubRun$choiceDispOnset + offset;
    onsetShift = onsetShift + offset
    onsetPOC = onsetPOC + offset
    
    # store onset, duration and modulation into a single data frame
    choiceMeanEV = cbind(onset, RDMsubRun$choiceDispDuration, modulationEV);
    #choiceGain = cbind(onset, duration, modulationGain);
    choiceEVG = cbind(onset, RDMsubRun$choiceDispDuration, modulationEVG);
    choiceSafe = cbind(onset, RDMsubRun$choiceDispDuration, modulationSafe);
    choiceNoModulation = cbind(onset, RDMsubRun$choiceDispDuration, 1); # gets a 1 for "weight" column since not using modulation here
    choiceChosenUnchosen = cbind(onset, RDMsubRun$choiceDispDuration, modulationChoseUnchosen)
    choiceShiftNoModulation = cbind(onsetShift, durationShift, 1); # gets a 1 for "weight" column since not using modulation here
    choiceShiftAmt = cbind(onsetShift, durationShift, modulationShift)
    choicePOCAmt = cbind(onsetPOC, durationPOC, modulationPOC)
    choiceRelEarnings = cbind(onset, RDMsubRun$choiceDispDuration, modulationRelEarnings)
    choiceLinear = cbind(onset,RDMsubRun$choiceDispDuration, modulationLinear)


    # create file names
    choiceMEVfileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("choiceDispMeanEV_run",r,sep=""));
    #choiceGAINfileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("choiceDispGainAmt_run",r,sep=""));
    choiceEVGfileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("choiceDispEVGAmt_run",r,sep=""));
    choiceSAFEfileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("choiceDispSafeAmt_run",r,sep=""));
    choiceNOMODfileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("choiceDispNoMod_run",r,sep=""));
    choiceChosenUnchosenfileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("choiceDispChosenUnchosen_run",r,sep=""))
    choiceShiftNoModfileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("choiceDispShiftNoMod_run",r,sep=""))
    choiceShiftAmtfileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("choiceDispShiftAmt_run",r,sep=""))
    
    choiceRelEarningsfileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("choiceRelEarnings_run",r,sep=""))
    choiceLinearfileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("choiceLinearTerm_run",r,sep=""))
    choicePastOutcomefileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("choicePastOutcome_run",r,sep=""))
    
    
    # save files
    write.table(choiceMeanEV, file=choiceMEVfileName, row.names = F, col.names = F, sep="\t");
    #write.table(choiceGain, file=choiceGAINfileName, row.names = F, col.names = F, sep="\t");
    write.table(choiceEVG, file=choiceEVGfileName, row.names = F, col.names = F, sep="\t");
    write.table(choiceSafe, file=choiceSAFEfileName, row.names = F, col.names = F, sep="\t");
    write.table(choiceNoModulation, file=choiceNOMODfileName, row.names = F, col.names = F, sep="\t");
    write.table(choiceChosenUnchosen, file=choiceChosenUnchosenfileName, row.names = F, col.names = F, sep="\t");
    write.table(choiceShiftNoModulation, file=choiceShiftNoModfileName, row.names = F, col.names = F, sep="\t");
    write.table(choiceShiftAmt, file=choiceShiftAmtfileName, row.names = F, col.names = F, sep="\t");
    write.table(choiceRelEarnings, file=choiceRelEarningsfileName, row.names = F, col.names = F, sep="\t");
    write.table(choiceLinear, file=choiceLinearfileName, row.names = F, col.names = F, sep="\t");
    write.table(choicePOCAmt, file=choicePastOutcomefileName, row.names = F, col.names = F, sep="\t");
    
    

  } # end for (r in 1:nRun)
} # end for (s in 1:nSubRaw)

```
  
  
  
#### Create onset files for OUTCOME
- outcomeDispNoMod_run#.txt : all outcomes, no modulation 
- outcomeDisp_otcAmt_run#.txt: all outcomes, outcome amount (mean centered within runs)
- outcomeDisp_otcWinAmt_run#.txt: win, received-not received (mean centered within runs; this is just the gain amount because loss is 0)
- outcomeDisp_otcLossAmt_run#.txt: loss, received-not received (mean centered within runs; because losses are 0, this may be more meaningful)
- outcomeDisp_otcSafeAmt_run#.txt: safe, amount received (mean centered within runs)
- outcomeDispEarnings_run#.txt: outcome display modulated by earnings (inc. outcome on current trial; mean centered ACROSS runs)


```{r outcome}



# each participant has three event files, one for each run
# each event file has 438 rows (73 trials x 6 events)
nTblock = 73;
nEvents = 6;
nRun = 3;
offset = .6087;
scaleby = max(RDMraw$riskyGain, na.rm=T);



for (s in 1:nSubRaw) {
  
  ind = grep(sprintf("sub-%s_run",subID_bids[s]), eventFiles); # get indices of event files for participant 
  RDMsub = RDMraw[RDMraw$subjectIndex==subNum[s],]; # load risky decision-making data
   
  for (r in 1:nRun){
    
    RDMsubRun = RDMsub[RDMsub$block==r,] # just get sub RDM data for this run
    eventrun = read.csv(eventFiles[ind[r]]); # load file for one run
    
   
    ###   OUTCOME    ###
    
    outcomeInd = which(eventrun$eventType=="outcome");  # index start of outcome display for all outcomes
    
    
    # set up onset and duration variables (still include missed trials at this point)
    outcomeDispOnset = eventrun$onset[outcomeInd]; # onset
    outcomeDispDuration = eventrun$duration[outcomeInd] # duration 
    
    # add onset and duration to RDM data
    RDMsubRun$outcomeDispOnset = outcomeDispOnset
    RDMsubRun$outcomeDispDuration = outcomeDispDuration

    
        #remove missed trials (for these timing files we are only accounting for choice display when choice was made - missed trials are accounted for down below in missed trial timing files)
    missedTrials = RDMsubRun$triBlock[is.na(RDMsubRun$choice)]; # index the missed trials for this run
    if(length(missedTrials>0)){
      RDMsubRun =RDMsubRun[-c(missedTrials),] # remove missed trials
      modulationAllotc = modulationAllotc[-c(missedTrials)]
    }

# for the EV that includes all trial types, we need to remove missed trials (missed Ts are already dealt with by the nature the gain/loss/safe outcome EVs)  
    # missedTrials = RDMsubRun$triBlock[is.na(RDMsubRun$choice)]; # index the missed trials for this run
    # if(length(missedTrials>0)){
    #   onsetAllotc = onsetAllotc[-c(missedTrials)]; # remove missed trials
    #   durationAllotc = durationAllotc[-c(missedTrials)]; # remove missed trials
    #   modulationAllotc = modulationAllotc[-c(missedTrials)]; # remove missed trials
    # }
    # 
    # index gain, loss and safe outcome trials
    gainOutcomeTrial = which(is.finite(RDMsubRun$outcome) & RDMsubRun$choice==1 & RDMsubRun$outcome==RDMsubRun$riskyGain);   # RDM trial number of gain outcome for block r
    lossOutcomeTrial = which(is.finite(RDMsubRun$outcome) & RDMsubRun$choice==1 & RDMsubRun$outcome==RDMsubRun$riskyLoss);   # RDM trial number of loss outcome for block r
    safeOutcomeTrial = which(is.finite(RDMsubRun$outcome) & RDMsubRun$choice==0 & RDMsubRun$outcome==RDMsubRun$alternative); # RDM trial number of safe outcome for block r
    # Used "is.finite()" above because otherwise its includes missed trials for each of these variables.
    # also added in RDMsub$choice==1 and 0 because some trials have safe and loss amounts that were both 0 on the same trial
    
    
        
 
    # modulations are mean-centered for each functional run for each participant
    # all outcomes
        modulationAllotc = RDMsubRun$outcome - mean(RDMsubRun$outcome); # outcome amount, mean centered within run
  
    
      # gain outcomes
        onsetGainotc = RDMsubRun$outcomeDispOnset[gainOutcomeTrial]; 
        durationGainotc = RDMsubRun$outcomeDispDuration[gainOutcomeTrial]; 
        modulationGainotc = RDMsubRun$outcome[gainOutcomeTrial] - mean(RDMsubRun$outcome[gainOutcomeTrial]); # mean center within run 
        
        
      # loss outcomes (received - not received)
        onsetLossotc = RDMsubRun$outcomeDispOnset[lossOutcomeTrial]; 
        durationLossotc = RDMsubRun$outcomeDispDuration[lossOutcomeTrial]; 
        # losses should be received - not received so 0 - gain amount on a loss trial
        modulationLossotc = (0 - RDMsubRun$riskyGain[lossOutcomeTrial]) - mean(0 - RDMsubRun$riskyGain[lossOutcomeTrial]); # mean centered within run
        
      # safe outcomes
        onsetSafeotc = RDMsubRun$outcomeDispOnset[safeOutcomeTrial]; 
        durationSafeotc = RDMsubRun$outcomeDispDuration[safeOutcomeTrial]; 
        modulationSafeotc = RDMsubRun$outcome[safeOutcomeTrial] - mean(RDMsubRun$outcome[safeOutcomeTrial]); # mean centered within run 
        
    
      # earnings 
        modulationEarningsTrialT = RDMsubRun$earningsTrialT - mean(RDMsub$earningsTrialT) # earnings including outcome on current trial mean centered ACROSS runs

        # round and scale the modulators
        modulationGainotc = round(modulationGainotc/scaleby, digits=2);
        modulationSafeotc = round(modulationSafeotc/scaleby, digits=2);
        modulationLossotc = round(modulationLossotc/scaleby, digits = 2);
        modulationAllotc = round(modulationAllotc/scaleby, digits =2)
        modulationEarningsTrialT = round(modulationEarningsTrialT, digits =2) # value already scaled 
          
    # Offset the onset times by .6087s (see notes above)
    onsetAllotc = RDMsubRun$outcomeDispOnset + offset;
    onsetGainotc = onsetGainotc + offset;
    onsetLossotc = onsetLossotc + offset;
    onsetSafeotc = onsetSafeotc + offset;
    
    

    
    # store onset, duration and modulation into a single data frame
    outcomeAmt = cbind(onsetAllotc, RDMsubRun$outcomeDispDuration, modulationAllotc);
    GAINoutcomeAmt = cbind(onsetGainotc, durationGainotc, modulationGainotc);
    LOSSoutcomeAmt = cbind(onsetLossotc, durationLossotc, modulationLossotc);
    SAFEoutcomeAmt = cbind(onsetSafeotc, durationSafeotc, modulationSafeotc);
    NOMODoutcomeAmt = cbind(onsetAllotc, RDMsubRun$outcomeDispDuration, 1);
    outcomeDispEarnings = cbind(onsetAllotc, RDMsubRun$outcomeDispDuration, modulationEarningsTrialT)
    
    # create file names
    outcomeAmtfileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("outcomeDispOCAmt_run",r,sep=""));
    GAINoutcomeAmtfileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("outcomeDispOCWinAmt_run",r,sep=""));
    LOSSoutcomeAmtfileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("outcomeDispOCLossAmt_run",r,sep=""));
    SAFEoutcomeAmtfileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("outcomeDispOCSafeAmt_run",r,sep=""));
    NOMODoutcomeAmtfileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("outcomeDispNoMod_run",r,sep=""));
    outcomeDispEarningsfileName =sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("outcomeDispEarnings_run",r,sep=""));
    # save files
    write.table(outcomeAmt, file=outcomeAmtfileName, row.names = F, col.names = F, sep="\t");
    write.table(GAINoutcomeAmt, file=GAINoutcomeAmtfileName, row.names = F, col.names = F, sep="\t");
    write.table(LOSSoutcomeAmt, file=LOSSoutcomeAmtfileName, row.names = F, col.names = F, sep="\t");
    write.table(SAFEoutcomeAmt, file=SAFEoutcomeAmtfileName, row.names = F, col.names = F, sep="\t");
    write.table(NOMODoutcomeAmt, file=NOMODoutcomeAmtfileName, row.names = F, col.names = F, sep="\t");
    write.table(outcomeDispEarnings, file = outcomeDispEarningsfileName, row.names = F, col.names = F, sep="\t")
    
  } # end for (r in 1:nRun)
} # end for (s in 1:nSubRaw)

```

#### Create onset files for DECISION
- decision_run#.txt: choice (generally)
- decisionGamble_run#.txt: chose gamble
- decisionSafe_run#.txt: choice safe

- create files that modulate decision by mean ev, risky gain and safe amounts


- ***big thing here is how to incorporate reaction time and does the timing add up between the event files (when the decision window ends) and reaction time in the choice set dataframe. For the decision time series, the onset of the choice will be the onset of the decision window + reaction time. The duration will be 0 seconds.

```{r decision}
# 
# # each participant has three event files, one for each run
# # each event file has 438 rows (73 trials x 6 events)
# nTblock = 73;
# nEvents = 6;
# nRun = 3;
# offset = .6087;
# scaleby = max(RDMraw$riskyGain, na.rm=T);
# 
# for (s in 1:nSubRaw) {
#   
#   ind = grep(sprintf("sub-%s_run",subID_bids[s]), eventFiles); # get indices of event files for participant 
#   RDMsub = RDMraw[RDMraw$subjectIndex==subNum[s],]; # load risky decision-making data
#    
#   for (r in 1:nRun){
#     
#     eventrun = read.csv(eventFiles[ind[r]]); # load file for one run
#     
#     ###   DECISION/RT    ###
#   
#     decisionInd = which(eventrun$eventType=="decisionWindow");  # index start of decision window
#     
#     
#         #we want only non-missed trials to be accounted for in these timing files
#     #missedTrials = RDMsub$triBlock[is.na(RDMsub$choice) & RDMsub$block==r]; # index the missed trials for this run
#     #if(length(missedTrials>0)){
#     #  decisionInd = decisionInd[-c(missedTrials)]; # remove missed trials
#     #}
# 
#     
#     
#     gambleTrial = RDMsub$triBlock[RDMsub$block==r & is.finite(RDMsub$choice) & RDMsub$choice==1];   # RDM trial number of gamble choice for block r
#     safeTrial = RDMsub$triBlock[RDMsub$block==r & is.finite(RDMsub$choice) & RDMsub$choice==0]; # RDM trial number of safe choice for block r    
#     
#     
#     # Store events by onset, duration and modulation (this looks a little different for each outcome onset file)
#     # mean center modulation within each functional run for each participant
#       # all decision types
#         onsetAllDecision = eventrun$onset[decisionInd] + RDMsub$RTs[RDMsub$block==r]; # onset is decision window onset + RTs
#         durationAllDecision = 0; # duration of decision will be 0
#         modulationEV = RDMsub$meanEV[RDMsub$block==r]- mean(RDMsub$meanEV[is.finite(RDMsub$choice) & RDMsub$block==r], na.rm=T); # mean EV
#         modulationGain = RDMsub$riskyGain[RDMsub$block==r]- mean(RDMsub$riskyGain[is.finite(RDMsub$choice) & RDMsub$block==r], na.rm=T); # risky gain amount
#         modulationSafe = RDMsub$alternative[RDMsub$block==r] - mean(RDMsub$alternative[is.finite(RDMsub$choice) & RDMsub$block==r], na.rm=T); # risky safe amount
#         modulationDecisionType = RDMsub$choice[RDMsub$block==r];
#         modulationDecisionType[modulationDecisionType==0] =-1; #change losses to be coded -1
#             
#       # gamble decision trials
#         onsetGambleDecision = onsetAllDecision[gambleTrial]; 
#         durationGambleDecision = 0; 
#         modulateGambleGain = modulationGain[gambleTrial]; # modulationGain is already mean-centered
#         modulateGambleSafe = modulationSafe[gambleTrial]; # modulationSafe is already mean-centered
#         modulateGambleEV = modulationEV[gambleTrial]; # modulcationEV is already mean centered
#         
# 
#       # safe decision trials
#         onsetSafeDecision = onsetAllDecision[safeTrial]; 
#         durationSafeDecision = 0; 
#         modulateSafeGain = modulationGain[safeTrial]; # modulationGain is already mean-centered
#         modulateSafeSafe = modulationSafe[safeTrial]; # modulationsafe is already mean-centered
#         modulateSafeEV = modulationEV[safeTrial]; # modulationEV is already mean-centered
#         
#         
#         # round and scale the modulators
#          modulationEV = round(modulationEV/scaleby, digits=2)
#          modulationGain= round(modulationGain/scaleby, digits=2)
#          modulationSafe= round(modulationSafe/scaleby, digits=2)
#          modulateGambleEV= round(modulateGambleEV/scaleby, digits=2)
#          modulateGambleGain= round(modulateGambleGain/scaleby, digits=2)
#          modulateGambleSafe= round(modulateGambleSafe/scaleby, digits=2)
#          modulateSafeEV= round(modulateSafeEV/scaleby, digits=2)
#          modulateSafeGain= round(modulateSafeGain/scaleby, digits=2)
#          modulateSafeSafe= round(modulateSafeSafe/scaleby, digits=2)
#          
#     # Offset the onset times by .6087s (see notes above)
#       onsetAllDecision = onsetAllDecision + offset
#       onsetGambleDecision = onsetGambleDecision + offset
#       onsetSafeDecision = onsetSafeDecision + offset
#       
#       
#     # for the EV that includes all trial types, we need to remove missed trials (missed Ts are already dealt with by the nature of subsetting the gamble/safe choices)
#     missedTrials = RDMsub$triBlock[is.na(RDMsub$choice) & RDMsub$block==r]; # index the missed trials for this run
#     if(length(missedTrials>0)){
#       onsetAllDecision = onsetAllDecision[-c(missedTrials)]; # remove missed trials
#       durationAllDecision = durationAllDecision[-c(missedTrials)]; # remove missed trials
#       modulationEV = modulationEV[-c(missedTrials)]; # remove missed trials
#       modulationGain = modulationGain[-c(missedTrials)]; # remove missed trials
#       modulationSafe = modulationSafe[-c(missedTrials)]; # remove missed trials on
#       modulationDecisionType = modulationDecisionType[-c(missedTrials)]
#     }
#     
#     # store onset, duration and modulation into a single data frame
#       decisionAllNoMod = cbind(onsetAllDecision, durationAllDecision,1); # 1 for parametric modulation
#       decisionAllType = cbind(onsetAllDecision, durationAllDecision,modulationDecisionType)
#       
#       EVdecisionAll   = cbind(onsetAllDecision, durationAllDecision, modulationEV);
#       GAINdecisionAll = cbind(onsetAllDecision, durationAllDecision, modulationGain);
#       SAFEdecisionAll = cbind(onsetAllDecision, durationAllDecision, modulationSafe);
#       
#       EVdecisionGamble =   cbind(onsetGambleDecision, durationGambleDecision, modulateGambleEV);
#       GAINdecisionGamble = cbind(onsetGambleDecision, durationGambleDecision, modulateGambleGain);
#       SAFEdecisionGamble = cbind(onsetGambleDecision, durationGambleDecision, modulateGambleSafe);
#       
#       EVdecisionSafe =  cbind(onsetSafeDecision, durationSafeDecision, modulateSafeEV);
#       GAINdecisionSafe = cbind(onsetSafeDecision, durationSafeDecision, modulateSafeGain); 
#       SAFEdecisionSafe = cbind(onsetSafeDecision, durationSafeDecision, modulateSafeSafe);
#     
# 
#     # create file names
#     decisionAllNOMODfileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("decisionAllNoMod_run",r,sep=""));
#     decisionAlltypefileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("decisionAllType_run",r,sep=""));
#     decisionAllmeanEVfileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("decisionAllMeanEVamt_run",r,sep=""));
#     decisionAllGainfileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("decisionAllGainAmt_run",r,sep=""));
#     decisionAllSafefileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("decisionAllSafeAmt_run",r,sep=""));  
#       
#     decisionGamblemeanEVfileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("decisionGambleMeanEVamt_run",r,sep=""));
#     decisionGambleGainfileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("decisionGambleGainAmt_run",r,sep=""));
#     decisionGambleSafefileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("decisionGambleSafeAmt_run",r,sep="")); 
#       
#     decisionSafemeanEVfileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("decisionSafeMeanEVamt_run",r,sep=""));
#     decisionSafeGainfileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("decisionSafeGainAmt_run",r,sep=""));
#     decisionSafeSafefileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("decisionSafeSafeAmt_run",r,sep=""));
#       
#       
#     # save files
#     write.table(decisionAllNoMod, file=decisionAllNOMODfileName, row.names = F, col.names = F, sep="\t");
#     write.table(decisionAllType, file=decisionAlltypefileName, row.names = F, col.names = F, sep="\t");
#     write.table(EVdecisionAll, file=decisionAllmeanEVfileName, row.names = F, col.names = F, sep="\t");
#     write.table(GAINdecisionAll, file=decisionAllGainfileName, row.names = F, col.names = F, sep="\t");
#     write.table(SAFEdecisionAll, file=decisionAllSafefileName, row.names = F, col.names = F, sep="\t");
#     
#     write.table(EVdecisionGamble, file=decisionGamblemeanEVfileName, row.names = F, col.names = F, sep="\t");
#     write.table(GAINdecisionGamble, file=decisionGambleGainfileName, row.names = F, col.names = F, sep="\t");
#     write.table(SAFEdecisionGamble, file=decisionGambleSafefileName, row.names = F, col.names = F, sep="\t");
#       
#     write.table(EVdecisionSafe, file=decisionSafemeanEVfileName, row.names = F, col.names = F, sep="\t");
#     write.table(GAINdecisionSafe, file=decisionSafeGainfileName, row.names = F, col.names = F, sep="\t");
#     write.table(SAFEdecisionSafe, file=decisionSafeSafefileName, row.names = F, col.names = F, sep="\t");
# 
#     
#   } # end for (r in 1:nRun)
# } # end for (s in 1:nSubRaw)

```

# Onset files for decision modulated by previous outcome amount
```{r decision-past-outcome-amt}
# # AT DECISION (I.E. ACTION), WHAT WAS PAST OUTCOME AMOUNT?
# 
# # In these timing files, we will exclude missed choices as well as choices that followed missed trials (i.e. there is no past outcome). We will be using these timing files with the timing file for decision + no modulation which will account for those trials where the previous trial was missed.
# 
# # create past outcome variable
# newMat = matrix(data=NA,nrow=nrow(RDMraw), ncol=2)
# newMat[,1] <- RDMraw$outcome; #take data from columns
# newMat[2:nrow(newMat),1] <- newMat[1:(nrow(newMat)-1),1]; # removes first row, shifts everything up
# newMat[1,1] <- NaN #put Nan in for first row (first trial for subject 1, bc there is no past trial)
# newMat[,2]<-c(0,diff(RDMraw$subjectIndex)); #put differences between NewSubjectIndex into newvector, 1s show up when subject changes
# newMat[newMat[,2]>0,]=NaN; #in newmtx, when diff = 1, replace with NaN, this replaces first trial with nan
# RDMraw$poc1 = newMat[,1];# add new vector to capData
# 
# 
# nTblock = 73;
# nEvents = 6;
# nRun = 3;
# offset = .6087;
# scaleby = max(RDMraw$riskyGain, na.rm=T);
# 
# for (s in 1:nSubRaw) {
#   
#   ind = grep(sprintf("sub-%s_run",subID_bids[s]), eventFiles); # get indices of event files for participant 
#   RDMsub = RDMraw[RDMraw$subjectIndex==subNum[s],]; # load risky decision-making data
#    
#   for (r in 1:nRun){
#     
#     eventrun = read.csv(eventFiles[ind[r]]); # load file for one run
#     
#     ###   DECISION/RT    ###
#   
#     decisionInd = which(eventrun$eventType=="decisionWindow");  # index start of decision window
#     
#     onsetAllDecision = eventrun$onset[decisionInd] + RDMsub$RTs[RDMsub$block==r]; # onset is decision window onset + RTs
#     durationAllDecision = 0; # duration of decision will be 0
#      
#     pocmean = mean(RDMsub$poc1[is.finite(RDMsub$poc1) & RDMsub$block==r],na.rm=T); 
#     modulationPOC = RDMsub$poc1[RDMsub$block==r] -pocmean #poc mean centered
#     modulationPOC = round(modulationPOC/scaleby, digits=2); # round and scale modulator
# 
#     # Offset the onset times by .6087s (see notes above)
#     onsetAllDecision = onsetAllDecision + offset
#     
#           
#     # for the EV that includes all trial types, we need to remove missed trials (missed Ts are already dealt with by the nature of subsetting the gamble/safe choices)
# 
#     missedPOC = RDMsub$triBlock[is.na(RDMsub$poc1) & RDMsub$block==r] # index NaN poc for this run
#     # if (length(missedPOC)>0){ # if a participant missed a trial
#     #   modulationPOC[missedPOC]=0-pocmean; # set the modulation of NAN poc trials to 0, mean center
#     # }; 
#     # 
# 
#     missedTrials = c(missedPOC, RDMsub$triBlock[is.na(RDMsub$choice) & RDMsub$block==r]) # index missed trials for this run, combine with trials with no POC
#      if(length(missedTrials>0)){
#       onsetAllDecision = onsetAllDecision[-c(missedTrials)]; # remove missed trials
#       modulationPOC = modulationPOC[-c(missedTrials)]; # remove missed trials
#     }
#     
# 
#     decisionPOCAmt = cbind(onsetAllDecision, durationAllDecision,modulationPOC); # modulated by outcome amount
# 
#     
#     # create file names
#     #decisionPOCNOMODfileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("decisionPOCnoMod_run",r,sep=""));
#     decisionPOCAmtfileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("decisionPOCAmt_run",r,sep=""));
# 
#      # save files
#     #write.table(decisionPOCnoMod, file=decisionPOCNOMODfileName, row.names = F, col.names = F, sep="\t");
#     write.table(decisionPOCAmt, file=decisionPOCAmtfileName, row.names = F, col.names = F, sep="\t");
#     
#     #MISSED TRIALS ARE THE SAME HERE AS SECTION BELOW (PREVIOUSLY THOUGHT THEY WERE DIFFERENT) - COMMENTING OUT
#    #  #MAKE MISSED TRIALS TIMING FILES: 
#    #    # these amount of missed trials for these files will be more than others because here we are excluding trials where poc =NaN and choice=NaN
#    #    # this means every participant will have a missed trial file for decision poc amount for the run because poc on trial 1= NaN.
#    #  
#    #  if(length(missedTrials>0)){ # for participants/runs with a missing trial
#    # 
#    #    # for missed trials in decision analyses, we want the choice display and response window
#    #    stimStartInd = which(eventrun$eventType=="stimulusStart");  # index start of stimulus display
#    #    stimStartInd = stimStartInd[missedTrials]; # just need index for missed trials
#    #    decWindowInd = which(eventrun$eventType=="decisionWindow"); # index start of decision window
#    #    decWindowInd = decWindowInd[missedTrials]; # just need index for missed trials
#    # 
#    #    # store events by onset, duration , and then modulation will =1
#    #    onset = eventrun$onset[stimStartInd]; # onset is stimStart onset
#    #    duration = eventrun$duration[stimStartInd] + eventrun$duration[decWindowInd]; # duration is stimStart duration + decisionWindow duration
#    # 
#    # 
#    #     # Offset the onset times by .6087s (see notes above)
#    #    onset = onset + offset;
#    # 
#    #  # store onset, duration and modulation into a single data frame
#    #  decisionPOCnoModMissT = cbind(onset, duration, 1); # gets a 1 for "weight" column since not using modulation here
#    #  
#    # decisionPOCnoModmissTfileName = sprintf("%s/sub-%s/%s.txt", config$path$data$missedTrials_files,subID_bids[s],paste("missT_decisionPOCnoMod_run",r,sep=""));
#    #      
#    #  # save files
#    #  write.table(decisionPOCnoModMissT, file=decisionPOCnoModmissTfileName, row.names = F, col.names = F, sep="\t");
#     
#     #} # end if(length(missedTrials>0))
# 
#     
#         
#         
#     
#     } # end for (r in 1:nRun)
# } # end for (s in 1:nSubRaw)
#   
# 


```




Create files for missed trials 
--> missed trials means participants did not respond at all or in time and during the outcome display, the message was "you did not respond in time"
--> depending on what GLM we are running, these missed trial files will be slightly different because we are going to use 3-column format that specifies the timing based on the event we are interestd in (e..g outcome vs. choice display)

Missed trial files will be 3 column like our other EVs. Participants who don't miss any trials will still have a 3-column EV file but it will be all zeroes.



```{r}

nTblock = 73;
nRun = 3;
offset = .6087;
scaleby = max(RDMraw$riskyGain, na.rm=T);

# FIRST: let's make missed trial timing files for participants' runs that did not have any missed trials.

# index sub IDs who missed trials 
subsWhoMissed = unique(RDMraw$subjectIndex[is.na(RDMraw$choice)]); # list sub IDs who missed at least one trial
nSubWhoMissed = length(subsWhoMissed);

for (s in 1:nSubRaw) {
  # the way we are indexing for this loop is slightly different from above

  ind = grep(sprintf("sub-%s_run",subID_bids[s]), eventFiles); # get indices of event files for participant 
  RDMsub = RDMraw[RDMraw$subjectIndex==subNum[s],]; # load risky decision-making data
  
  # determine which runs have missed trials
  runsWithMissT = unique(RDMsub$block[is.na(RDMsub$choice)]);
  
  # if participant did not miss any trials across any runs:
  if (length(runsWithMissT)==0){
    noMissT = matrix(data=0, nrow=nTblock,ncol=3)
    
    missTrun1fileName = sprintf("%s/sub-%s/%s.txt", config$path$data$missedTrials_files,subID_bids[s],"noMissedTrials_run1");
    missTrun2fileName = sprintf("%s/sub-%s/%s.txt", config$path$data$missedTrials_files,subID_bids[s],"noMissedTrials_run2");
    missTrun3fileName = sprintf("%s/sub-%s/%s.txt", config$path$data$missedTrials_files,subID_bids[s],"noMissedTrials_run3");
    
    write.table(noMissT, file=missTrun1fileName, row.names = F, col.names = F, sep="\t");
    write.table(noMissT, file=missTrun2fileName, row.names = F, col.names = F, sep="\t");
    write.table(noMissT, file=missTrun3fileName, row.names = F, col.names = F, sep="\t");
    
  } else {
    
    runs = c(1,2,3);
    noMissRuns = runs[-c(runsWithMissT)]; # runs that have no missed trials
    
    if (length(noMissRuns)>0){
      for (m in 1:length(noMissRuns)){ # for all runs without a missed trial, make the 3-column zero timing files
        noMissT = matrix(data=0, nrow=nTblock, ncol=3)  
        missTrunFilename = sprintf("%s/sub-%s/noMissedTrials_run%s.txt", config$path$data$missedTrials_files,subID_bids[s], noMissRuns[m]);
        
        write.table(noMissT, file=missTrunFilename, row.names = F, col.names = F, sep="\t");
        
      } # for (m in 1:length(noMissRuns))
      
    }# if (length(noMissRuns)>0)
    
  } # if(length(runsWith...))
} # end for (s in 1:nSubRaw)



# Then for the TIMING FILES WHERE WE NEED TO ACCOUNT FOR MISSED TRIALS: we will make them based on the analysis we are interested in.

# CHOICE DISPLAY NO MODULATION:
for (s in 1:nSubWhoMissed) {  # for participants with missed trials
  
  # the way we are indexing for this loop is slightly different from above
  if (subsWhoMissed[s]>=10){
      sub_id_bid_format = sprintf("0%s", subsWhoMissed[s])
  } else {
      sub_id_bid_format = sprintf("00%s", subsWhoMissed[s])
  }
  
  
  ind = grep(sprintf("sub-%s_run",sub_id_bid_format), eventFiles); # get indices of event files for participant 

  #ind = grep(sub_id_bid_format,eventFiles)
  
  RDMsub = RDMraw[RDMraw$subjectIndex==subsWhoMissed[s],]; # load risky decision-making data
  
  # determine which runs have missed trials
  runsWithMissT = unique(RDMsub$block[is.na(RDMsub$choice)]);
  
  for (r in 1:length(runsWithMissT)){
    
    # determine which trials were missed within run
    missTind = RDMsub$triBlock[is.na(RDMsub$choice) & RDMsub$block==runsWithMissT[r]]
    
    eventrun = read.csv(eventFiles[ind[runsWithMissT[r]]]); # load event file for one run


    stimStartInd = which(eventrun$eventType=="stimulusStart");  # index start of stimulus display
    stimStartInd = stimStartInd[missTind]; # just need index for missed trials
    decWindowInd = which(eventrun$eventType=="decisionWindow"); # index start of decision window    
    decWindowInd = decWindowInd[missTind]; # just need index for missed trials
    
    # store events by onset, duration and modulation (mean ev, gain, safe) and mean center them (by functional run)
    onset = eventrun$onset[stimStartInd]; # onset is stimStart onset
    duration = eventrun$duration[stimStartInd] + eventrun$duration[decWindowInd]; # duration is stimStart duration + decisionWindow duration
    
    
     # Offset the onset times by .6087s (see notes above)
    onset = onset + offset;
    
    
    # store onset, duration and modulation into a single data frame
    choiceNoModulationMissT = cbind(onset, duration, 1); # gets a 1 for "weight" column since not using modulation here
    
    choiceNOMODmissTfileName = sprintf("%s/sub-%s/%s.txt", config$path$data$missedTrials_files,sub_id_bid_format,paste("missT_choiceDispNoMod_run",runsWithMissT[r],sep=""));
        
    # save files
    write.table(choiceNoModulationMissT, file=choiceNOMODmissTfileName, row.names = F, col.names = F, sep="\t");
    
        
  }# end for (r in 1:length(runsWithMissT)
} # end (s in 1:nSubWhoMissed)


# DECISION WINDOW NO MODULATION: ACTUALLY MAY NOT BE USING THIS FOR MISSED DECISION TIMING FILES
#   using choice display no mod missed trials made above because here we want to account for that 4s window to account for the visual information (and possible cognitive processing that just didn’t arrive at a choice in time)

# for (s in 1:nSubWhoMissed) {  # for participants with missed trials
#   
#   # the way we are indexing for this loop is slightly different from above
#   if (subsWhoMissed[s]>=10){
#       sub_id_bid_format = sprintf("0%s", subsWhoMissed[s])
#   } else {
#       sub_id_bid_format = sprintf("00%s", subsWhoMissed[s])
#   }
#   
#   
#   ind = grep(sprintf("sub-%s_run",sub_id_bid_format), eventFiles); # get indices of event files for participant 
# 
#   #ind = grep(sub_id_bid_format,eventFiles)
#   
#   RDMsub = RDMraw[RDMraw$subjectIndex==subsWhoMissed[s],]; # load risky decision-making data
#   
#   # determine which runs have missed trials
#   runsWithMissT = unique(RDMsub$block[is.na(RDMsub$choice)]);
#   
#   for (r in 1:length(runsWithMissT)){
#     
#     # determine which trials were missed within run
#     missTind = RDMsub$triBlock[is.na(RDMsub$choice) & RDMsub$block==runsWithMissT[r]]
#     
#     eventrun = read.csv(eventFiles[ind[runsWithMissT[r]]]); # load event file for one run
# 
#     
#     decisionInd = which(eventrun$eventType=="decisionWindow");  # index start of decision window
#     decisionInd = decisionInd[missTind]; # index just missed trials
# 
#     # Store events by onset, duration and modulation (this looks a little different for each outcome onset file)
#     # mean center modulation within each functional run for each participant
#       # all decision types
#         onsetAllDecision = eventrun$onset[decisionInd] + eventrun$duration[decisionInd]  # start of decision window for missed trials does not include RT so we mark the onset by the end of the decision window
#         duration = 0; # duration of decision will be 0
#     
#       # Offset the onset times by .6087s (see notes above)
#         onset = onsetAllDecision + offset
#     
#         decisionAllNoMod = cbind(onset,duration,1); # parametric modulation = 1
#         
#     # file name for decision    
#     decisionWindNOMODmissTfileName = sprintf("%s/sub-%s/%s.txt", config$path$data$missedTrials_files,sub_id_bid_format,paste("missT_decisionAllNoMod_run",runsWithMissT[r],sep=""));
#         
#     # save files
#     write.table(decisionAllNoMod, file=decisionWindNOMODmissTfileName, row.names = F, col.names = F, sep="\t");
#         
#   }# end for (r in 1:length(runsWithMissT)
# } # end (s in 1:nSubWhoMissed)




# OUTCOME DISPLAY NO MODULATION:
for (s in 1:nSubWhoMissed) {  # for participants with missed trials
  
  # the way we are indexing for this loop is slightly different from above
  if (subsWhoMissed[s]>=10){
      sub_id_bid_format = sprintf("0%s", subsWhoMissed[s])
  } else {
      sub_id_bid_format = sprintf("00%s", subsWhoMissed[s])
  }
  
  
  ind = grep(sprintf("sub-%s_run",sub_id_bid_format), eventFiles); # get indices of event files for participant 

  #ind = grep(sub_id_bid_format,eventFiles)
  
  RDMsub = RDMraw[RDMraw$subjectIndex==subsWhoMissed[s],]; # load risky decision-making data
  
  # determine which runs have missed trials
  runsWithMissT = unique(RDMsub$block[is.na(RDMsub$choice)]);
  
  for (r in 1:length(runsWithMissT)){
    
    # determine which trials were missed within run
    missTind = RDMsub$triBlock[is.na(RDMsub$choice) & RDMsub$block==runsWithMissT[r]]
    
    eventrun = read.csv(eventFiles[ind[runsWithMissT[r]]]); # load event file for one run

    
    outcomeInd = which(eventrun$eventType=="outcome");  # index start of decision window
    outcomeInd = outcomeInd[missTind]; # index just missed trials

    # Store events by onset, duration and modulation 
        onsetAllOutcomes = eventrun$onset[outcomeInd] 
        duration = eventrun$duration[outcomeInd]
    
      # Offset the onset times by .6087s (see notes above)
        onset = onsetAllOutcomes + offset
    
        outcomeDispNoMod = cbind(onset,duration,1); # parametric modulation = 1
        
    # file name for outcome 
    outcomeDispNOMODmissTfileName = sprintf("%s/sub-%s/%s.txt", config$path$data$missedTrials_files,sub_id_bid_format,paste("missT_outcomeDispNoMod_run",runsWithMissT[r],sep=""));
        
    # save files
    write.table(outcomeDispNoMod, file=outcomeDispNOMODmissTfileName, row.names = F, col.names = F, sep="\t");
        
  }# end for (r in 1:length(runsWithMissT)
} # end (s in 1:nSubWhoMissed)


```


