---
title: "createEventFiles"
author: "Hayley Brooks"
date: "5/27/2021"
output: html_document
---
##### Output:
  - An onset/timing file for each event on each run (3) for every participant (51)
  - events we are modeling for now: choice option display, decision, outcome, modulated by monetary amounts

##### Timing information
-Choice options were displayed for 2 seconds (forced viewing) then participants had 2 seconds to respond. Once they responded, the ISI (varied 1.75s-5.75s) began and anytime remaining in the 2 second response window was added to the ITI at the end of the trial. After the ISI, the outcome was shown for 1 second followed by the ITI (varied .75 - 4.75 plus the leftover response time (2-RT) ). ITI, ISI and RT are included in the raw dataset loaded below.

- There was a 15 second fixation at the start of each block (to allow the scanner to settle). The first trial started immediately after the fixation ended.

- parametric modulations are mean-centered for each functional run for each participant


#### Set up
```{r}
rm(list=ls());  # clear environment


library("config");
config <- config::get();

# load timing files:
eventFilePath = file.path(config$path$data$event_files); # location of event files for each participant and each run
eventFiles = list.files(eventFilePath, pattern= "*_event.csv", full.names = T); # store names of files that we will need

# load raw dataset for choiceset
RDMgroupCSVpath = file.path(config$path$data$raw_group,config$csvs$RDM_group_raw_csv);
RDMraw = read.csv(RDMgroupCSVpath); 

# Remove participant 13 (did not start risky decision-making task)
RDMraw = RDMraw[RDMraw$subjectIndex!=13,]
```

#### Subject Information
```{r}
subNum = unique(RDMraw$subjectIndex);
nSubRaw = length(subNum); # should be 51

# Create a vector that has the sub IDs formatted as in BIDS (e.g. 001, 002)
subID_bids = vector(); # create empty vector

for (s in 1: nSubRaw){
  if(s<10){
   subID_bids[s]=paste("00",subNum[s],sep="")
  }
  else {
   subID_bids[s]=paste("0", subNum[s],sep="")
  }
};



```

#### Create txt files
For a given trial, there are 5 events: choice display, choice/RT, ISI, outcome, ITI and 73 trials in each run for a total of 365 events in a run (1095 total events across all three runs because 5 x 219 = 1095);

We had a 15 second delay which = 32.6087 TRs, so we will delete 32 volumes in FSL and will need to adjust the timing files by .6087 seconds. From FSL: "remember when setting up the design matrix that the timings in the design matrix start at t=0 seconds, and this corresponds to the start of the first image taken after the deleted scans. In other words, the design matrix starts after the deleted scans have been deleted.""

To create the onset files for FSL, we use timing information from the sub_0##_run#_event.csv files which were created using the timing output from the study sessions. We will start each trial with stimulus start (not trial start) because there is a very slight delay between trial start and stimulus start (trial starts, computer randomly decides location of gamble/safe location on screen, then shows the stimuli)

We will be combining duration for stimulus and decision window because these are identical with the exception that participants were allowed to respond once the decision window started.

For modeling decision(action), it would be when RT happened in the time series (not RTs themselves)

When done, add these timing files to RDAC.


#### Create onset files for CHOICE DISPLAY

- choiceDisp_meanEV_run#.txt: choice display modulated by mean expected value
- choiceDisp_gainAmt_run#.txt: choice display modulated by gain amount (mean center?)
- choiceDisp_safeAmt_run#.txt: choice display modulated by safe amount (mean center?)


```{r} 

# Onset file names (will dynamically add run number once files are created)
#outcomeOnsetFileNames = c("outcomeDisp_otcAmt_run","outcomeDisp_otcWinAmt_run", "outcomeDisp_otcLossAmt_run", "outcomeDisp_otcSafeAmt_run");
#decisionOnsetFileNames = c("decision_run", "decisionGamble_run", "decisionSafe_run");

# each participant has three event files, one for each run
# each event file has 438 rows (73 trials x 6 events)
nTblock = 73;
nEvents = 6;
nRun = 3;
offset = .6087;

for (s in 1:nSubRaw) {
  
  ind = grep(sprintf("sub-%s_run",subID_bids[s]), eventFiles); # get indices of event files for participant 
  RDMsub = RDMraw[RDMraw$subjectIndex==subNum[s],]; # load risky decision-making data
   
  
  
  for (r in 1:nRun){
    
    eventrun = read.csv(eventFiles[ind[r]]); # load  event file for one run
    

    ###   CHOICE DISPLAY ###
    stimStartInd = which(eventrun$eventType=="stimulusStart");  # index start of stimulus display
    decWindowInd = which(eventrun$eventType=="decisionWindow"); # index start of decision window
    
    
    #we want only non-missed trials to be accounted for in these timing files
    missedTrials = RDMsub$triBlock[is.na(RDMsub$choice) & RDMsub$block==r]; # index the missed trials for this run
    if(length(missedTrials>0)){
      stimStartInd = stimStartInd[-c(missedTrials)]; # remove missed trials
      decWindowInd = decWindowInd[-c(missedTrials)]; # remove missed trials
    }


    # store events by onset, duration and modulation (mean ev, gain, safe) and mean center them (by functional run)
    onset = eventrun$onset[stimStartInd]; # onset is stimStart onset
    duration = eventrun$duration[stimStartInd] + eventrun$duration[decWindowInd]; # duration is stimStart duration + decisionWindow duration (which is basically RT)
    
    modulationEV = RDMsub$meanEV[is.finite(RDMsub$choice) & RDMsub$block==r]- mean(RDMsub$meanEV[is.finite(RDMsub$choice) & RDMsub$block==r], na.rm=T); # mean EV
    modulationGain = RDMsub$riskyGain[is.finite(RDMsub$choice) & RDMsub$block==r]-mean(RDMsub$riskyGain[is.finite(RDMsub$choice) & RDMsub$block==r], na.rm=T); # risky gain amount
    modulationSafe = RDMsub$alternative[is.finite(RDMsub$choice) & RDMsub$block==r]-mean(RDMsub$alternative[is.finite(RDMsub$choice) & RDMsub$block==r], na.rm=T); # safe amount
    
   # round modulators
    modulationEV = round(modulationEV, digits =2);
    modulationGain = round(modulationGain, digits =2);
    modulationSafe = round(modulationSafe, digits =2);
    
    
    # Offset the onset times by .6087s (see notes above)
    onset = onset + offset;
    
    
    # store onset, duration and modulation into a single data frame
    choiceMeanEV = cbind(onset, duration, modulationEV);
    choiceGain = cbind(onset, duration, modulationGain);
    choiceSafe = cbind(onset, duration, modulationSafe);
    choiceNoModulation = cbind(onset, duration, 1); # gets a 1 for "weight" column since not using modulation here
    
    # create file names
    choiceMEVfileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("choiceDisp_meanEV_run",r,sep=""));
    choiceGAINfileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("choiceDisp_gainAmt_run",r,sep=""));
    choiceSAFEfileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("choiceDisp_safeAmt_run",r,sep=""));
    
    choiceNOMODfileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("choiceDisp_noModulation_run",r,sep=""));
        
    # save files
    write.table(choiceMeanEV, file=choiceMEVfileName, row.names = F, col.names = F, sep="\t");
    write.table(choiceGain, file=choiceGAINfileName, row.names = F, col.names = F, sep="\t");
    write.table(choiceSafe, file=choiceSAFEfileName, row.names = F, col.names = F, sep="\t");
    write.table(choiceNoModulation, file=choiceNOMODfileName, row.names = F, col.names = F, sep="\t");
    
  } # end for (r in 1:nRun)
} # end for (s in 1:nSubRaw)

```
  
  
  
#### Create onset files for OUTCOME
- outcomeDisp_otcAmt_run#.txt: all outcomes, outcome amount
- outcomeDisp_otcWinAmt_run#.txt: win, received - not received 
- outcomeDisp_otcLossAmt_run#.txt: loss, received - not received
- outcomeDisp_otcSafeAmt_run#.txt: safe, amount received 

```{r}



# each participant has three event files, one for each run
# each event file has 438 rows (73 trials x 6 events)
nTblock = 73;
nEvents = 6;
nRun = 3;
offset = .6087;

for (s in 1:nSubRaw) {
  
  ind = grep(sprintf("sub-%s_run",subID_bids[s]), eventFiles); # get indices of event files for participant 
  RDMsub = RDMraw[RDMraw$subjectIndex==subNum[s],]; # load risky decision-making data
   
  for (r in 1:nRun){
    
    eventrun = read.csv(eventFiles[ind[r]]); # load file for one run
    
   
    ###   OUTCOME    ###
    
    outcomeInd = which(eventrun$eventType=="outcome");  # index start of outcome display for all outcomes
    
    
    #we want only non-missed trials to be accounted for in these timing files
    #missedTrials = RDMsub$triBlock[is.na(RDMsub$choice) & RDMsub$block==r]; # index the missed trials for this run
    #if(length(missedTrials>0)){
    #  outcomeInd = outcomeInd[-c(missedTrials)]; # remove missed trials
    #}


    
    gainOutcomeTrial = RDMsub$triBlock[RDMsub$block==r & is.finite(RDMsub$outcome) & RDMsub$choice==1 & RDMsub$outcome==RDMsub$riskyGain];   # RDM trial number of gain outcome for block r
    lossOutcomeTrial = RDMsub$triBlock[RDMsub$block==r & is.finite(RDMsub$outcome) & RDMsub$choice==1 & RDMsub$outcome==RDMsub$riskyLoss];   # RDM trial number of loss outcome for block r
    safeOutcomeTrial = RDMsub$triBlock[RDMsub$block==r & is.finite(RDMsub$outcome) & RDMsub$choice==0 & RDMsub$outcome==RDMsub$alternative]; # RDM trial number of safe outcome for block r
    # Used "is.finite()" above because otherwise its includes missed trials for each of these variables.
    # also added in RDMsub$choice==1 and 0 because some trials have safe and loss amounts that were both 0 on the same trial
    
    
    # Store events by onset, duration and modulation (this looks a little different for each outcome onset file)
    # modulations are mean-centered for each functional run for each participant
      # all outcomes
        onsetAllotc = eventrun$onset[outcomeInd]; # onset is outcome onset
        durationAllotc = eventrun$duration[outcomeInd]; # duration is outcome duration
        modulationAllotc = RDMsub$outcome[outcomeInd & RDMsub$block==r] - mean(RDMsub$outcome[is.finite(RDMsub$choice) & RDMsub$block==r]); # outcome amount
      
      # gain outcomes
        onsetGainotc = onsetAllotc[gainOutcomeTrial]; 
        durationGainotc = durationAllotc[gainOutcomeTrial]; 
        modulationGainotc = modulationAllotc[gainOutcomeTrial]; # modulationAllotc is already mean-centered
        
        
      # loss outcomes
        onsetLossotc = onsetAllotc[lossOutcomeTrial]; 
        durationLossotc = durationAllotc[lossOutcomeTrial]; 
        modulationLossotc = 1; # because this is always 0 in this task, we want to make this 1 for FSL timing files
        
        
      # safe outcomes
        onsetSafeotc = onsetAllotc[safeOutcomeTrial]; 
        durationSafeotc = durationAllotc[safeOutcomeTrial]; 
        modulationSafeotc = modulationAllotc[safeOutcomeTrial]; # modulationAllotc is already mean-centered
        
        # round the modulators
        modulationGainotc = round(modulationGainotc, digits=2);
        modulationSafeotc = round(modulationSafeotc, digits=2);
        modulationAllotc = round(modulationAllotc, digits =2)
          
    # Offset the onset times by .6087s (see notes above)
    onsetAllotc = onsetAllotc + offset;
    onsetGainotc = onsetGainotc + offset;
    onsetLossotc = onsetLossotc + offset;
    onsetSafeotc = onsetSafeotc + offset;
    
    
    # for the EV that includes all trial types, we need to remove missed trials (missed Ts are already dealt with by the nature the gain/loss/safe outcome EVs)  
    missedTrials = RDMsub$triBlock[is.na(RDMsub$choice) & RDMsub$block==r]; # index the missed trials for this run
    if(length(missedTrials>0)){
      onsetAllotc = onsetAllotc[-c(missedTrials)]; # remove missed trials
      durationAllotc = durationAllotc[-c(missedTrials)]; # remove missed trials
      modulationAllotc = modulationAllotc[-c(missedTrials)]; # remove missed trials
    }
    
    # store onset, duration and modulation into a single data frame
    outcomeAmt = cbind(onsetAllotc, durationAllotc, modulationAllotc);
    GAINoutcomeAmt = cbind(onsetGainotc, durationGainotc, modulationGainotc);
    LOSSoutcomeAmt = cbind(onsetLossotc, durationLossotc, modulationLossotc);
    SAFEoutcomeAmt = cbind(onsetSafeotc, durationSafeotc, modulationSafeotc);
    NOMODoutcomeAmt = cbind(onsetAllotc, durationAllotc, 1);
    
    # create file names
    outcomeAmtfileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("outcomeDisp_otcAmt_run",r,sep=""));
    GAINoutcomeAmtfileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("outcomeDisp_otcWinAmt_run",r,sep=""));
    LOSSoutcomeAmtfileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("outcomeDisp_otcLossAmt_run",r,sep=""));
    SAFEoutcomeAmtfileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("outcomeDisp_otcSafeAmt_run",r,sep=""));
    NOMODoutcomeAmtfileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("outcomeDisp_noModulation_run",r,sep=""));

    # save files
    write.table(outcomeAmt, file=outcomeAmtfileName, row.names = F, col.names = F, sep="\t");
    write.table(GAINoutcomeAmt, file=GAINoutcomeAmtfileName, row.names = F, col.names = F, sep="\t");
    write.table(LOSSoutcomeAmt, file=LOSSoutcomeAmtfileName, row.names = F, col.names = F, sep="\t");
    write.table(SAFEoutcomeAmt, file=SAFEoutcomeAmtfileName, row.names = F, col.names = F, sep="\t");
    write.table(NOMODoutcomeAmt, file=NOMODoutcomeAmtfileName, row.names = F, col.names = F, sep="\t");
    
  } # end for (r in 1:nRun)
} # end for (s in 1:nSubRaw)

```

#### Create onset files for DECISION
- decision_run#.txt: choice (generally)
- decisionGamble_run#.txt: chose gamble
- decisionSafe_run#.txt: choice safe

- create files that modulate decision by mean ev, risky gain and safe amounts


- ***big thing here is how to incorporate reaction time and does the timing add up between the event files (when the decision window ends) and reaction time in the choice set dataframe. For the decision time series, the onset of the choice will be the onset of the decision window + reaction time. The duration will be 0 seconds.



```{r}

# each participant has three event files, one for each run
# each event file has 438 rows (73 trials x 6 events)
nTblock = 73;
nEvents = 6;
nRun = 3;
offset = .6087;

for (s in 1:nSubRaw) {
  
  ind = grep(sprintf("sub-%s_run",subID_bids[s]), eventFiles); # get indices of event files for participant 
  RDMsub = RDMraw[RDMraw$subjectIndex==subNum[s],]; # load risky decision-making data
   
  for (r in 1:nRun){
    
    eventrun = read.csv(eventFiles[ind[r]]); # load file for one run
    
    ###   DECISION/RT    ###
  
    decisionInd = which(eventrun$eventType=="decisionWindow");  # index start of decision window
    
    
        #we want only non-missed trials to be accounted for in these timing files
    #missedTrials = RDMsub$triBlock[is.na(RDMsub$choice) & RDMsub$block==r]; # index the missed trials for this run
    #if(length(missedTrials>0)){
    #  decisionInd = decisionInd[-c(missedTrials)]; # remove missed trials
    #}

    
    
    gambleTrial = RDMsub$triBlock[RDMsub$block==r & is.finite(RDMsub$choice) & RDMsub$choice==1];   # RDM trial number of gamble choice for block r
    safeTrial = RDMsub$triBlock[RDMsub$block==r & is.finite(RDMsub$choice) & RDMsub$choice==0]; # RDM trial number of safe choice for block r    
    
    
    # Store events by onset, duration and modulation (this looks a little different for each outcome onset file)
    # mean center modulation within each functional run for each participant
      # all decision types
        onsetAllDecision = eventrun$onset[decisionInd] + RDMsub$RTs[RDMsub$block==r]; # onset is decision window onset + RTs
        durationAllDecision = 0; # duration of decision will be 0
        modulationEV = RDMsub$meanEV[RDMsub$block==r]- mean(RDMsub$meanEV[is.finite(RDMsub$choice) & RDMsub$block==r], na.rm=T); # mean EV
        modulationGain = RDMsub$riskyGain[RDMsub$block==r]- mean(RDMsub$riskyGain[is.finite(RDMsub$choice) & RDMsub$block==r], na.rm=T); # risky gain amount
        modulationSafe = RDMsub$alternative[RDMsub$block==r] - mean(RDMsub$alternative[is.finite(RDMsub$choice) & RDMsub$block==r], na.rm=T); # risky safe amount
            
      # gamble decision trials
        onsetGambleDecision = onsetAllDecision[gambleTrial]; 
        durationGambleDecision = 0; 
        modulateGambleGain = modulationGain[gambleTrial]; # modulationGain is already mean-centered
        modulateGambleSafe = modulationSafe[gambleTrial]; # modulationSafe is already mean-centered
        modulateGambleEV = modulationEV[gambleTrial]; # modulcationEV is already mean centered
        

      # safe decision trials
        onsetSafeDecision = onsetAllDecision[safeTrial]; 
        durationSafeDecision = 0; 
        modulateSafeGain = modulationGain[safeTrial]; # modulationGain is already mean-centered
        modulateSafeSafe = modulationSafe[safeTrial]; # modulationsafe is already mean-centered
        modulateSafeEV = modulationEV[safeTrial]; # modulationEV is already mean-centered
        
        
        # round the modulators
         modulationEV = round(modulationEV, digits=2)
         modulationGain= round(modulationGain, digits=2)
         modulationSafe= round(modulationSafe, digits=2)
         modulateGambleEV= round(modulateGambleEV, digits=2)
         modulateGambleGain= round(modulateGambleGain, digits=2)
         modulateGambleSafe= round(modulateGambleSafe, digits=2)
         modulateSafeEV= round(modulateSafeEV, digits=2)
         modulateSafeGain= round(modulateSafeGain, digits=2)
         modulateSafeSafe= round(modulateSafeSafe, digits=2)
         
    # Offset the onset times by .6087s (see notes above)
      onsetAllDecision = onsetAllDecision + offset
      onsetGambleDecision = onsetGambleDecision + offset
      onsetSafeDecision = onsetSafeDecision + offset
      
      
    # for the EV that includes all trial types, we need to remove missed trials (missed Ts are already dealt with by the nature of subsetting the gamble/safe choices)
    missedTrials = RDMsub$triBlock[is.na(RDMsub$choice) & RDMsub$block==r]; # index the missed trials for this run
    if(length(missedTrials>0)){
      onsetAllDecision = onsetAllDecision[-c(missedTrials)]; # remove missed trials
      durationAllDecision = durationAllDecision[-c(missedTrials)]; # remove missed trials
      modulationEV = modulationEV[-c(missedTrials)]; # remove missed trials
      modulationGain = modulationGain[-c(missedTrials)]; # remove missed trials
      modulationSafe = modulationSafe[-c(missedTrials)]; # remove missed trials on
    }
    
    # store onset, duration and modulation into a single data frame
      EVdecisionAll   = cbind(onsetAllDecision, durationAllDecision, modulationEV);
      GAINdecisionAll = cbind(onsetAllDecision, durationAllDecision, modulationGain);
      SAFEdecisionAll = cbind(onsetAllDecision, durationAllDecision, modulationSafe);
      
      EVdecisionGamble =   cbind(onsetGambleDecision, durationGambleDecision, modulateGambleEV);
      GAINdecisionGamble = cbind(onsetGambleDecision, durationGambleDecision, modulateGambleGain);
      SAFEdecisionGamble = cbind(onsetGambleDecision, durationGambleDecision, modulateGambleSafe);
      
      EVdecisionSafe =  cbind(onsetSafeDecision, durationSafeDecision, modulateSafeEV);
      GAINdecisionSafe = cbind(onsetSafeDecision, durationSafeDecision, modulateSafeGain); 
      SAFEdecisionSafe = cbind(onsetSafeDecision, durationSafeDecision, modulateSafeSafe);
    
    # create file names
    
    # create file names
    decisionAllmeanEVfileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("decisionAll_meanEVamt_run",r,sep=""));
    decisionAllGainfileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("decisionAll_gainAmt_run",r,sep=""));
    decisionAllSafefileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("decisionAll_safeAmt_run",r,sep=""));  
      
    decisionGamblemeanEVfileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("decisionGamble_meanEVamt_run",r,sep=""));
    decisionGambleGainfileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("decisionGamble_gainAmt_run",r,sep=""));
    decisionGambleSafefileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("decisionGamble_safeAmt_run",r,sep="")); 
      
    decisionSafemeanEVfileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("decisionSafe_meanEVamt_run",r,sep=""));
    decisionSafeGainfileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("decisionSafe_gainAmt_run",r,sep=""));
    decisionSafeSafefileName = sprintf("%s/sub-%s/%s.txt", config$path$data$onset_files,subID_bids[s],paste("decisionSafe_safeAmt_run",r,sep=""));
      
      
    # save files
    write.table(EVdecisionAll, file=decisionAllmeanEVfileName, row.names = F, col.names = F, sep="\t");
    write.table(GAINdecisionAll, file=decisionAllGainfileName, row.names = F, col.names = F, sep="\t");
    write.table(SAFEdecisionAll, file=decisionAllSafefileName, row.names = F, col.names = F, sep="\t");
    
    write.table(EVdecisionGamble, file=decisionGamblemeanEVfileName, row.names = F, col.names = F, sep="\t");
    write.table(GAINdecisionGamble, file=decisionGambleGainfileName, row.names = F, col.names = F, sep="\t");
    write.table(SAFEdecisionGamble, file=decisionGambleSafefileName, row.names = F, col.names = F, sep="\t");
      
    write.table(EVdecisionSafe, file=decisionSafemeanEVfileName, row.names = F, col.names = F, sep="\t");
    write.table(GAINdecisionSafe, file=decisionSafeGainfileName, row.names = F, col.names = F, sep="\t");
    write.table(SAFEdecisionSafe, file=decisionSafeSafefileName, row.names = F, col.names = F, sep="\t");

    
  } # end for (r in 1:nRun)
} # end for (s in 1:nSubRaw)

```

Create files for missed trials 
--> missed trials means participants did not respond at all or in time and during the outcome display, the message was "you did not respond in time"
--> depending on what GLM we are running, these missed trial files will be slightly different because we are going to use 3-column format that specifies the timing based on the event we are interestd in (e..g outcome vs. choice display)

Missed trial files will be 3 column like our other EVs. We will skip participants who don't have missed trials (this may change)

For now, create missed trial files for choice onset display - no parametric modulation

NEED TO UPDATE: Missed trial dummy EV files will need to be used for the following:
1) valuation period modulated by mean EV 
2) valuation period modulated by risky gain 
3) valuation period modulated by safe 
4) outcome modulated by all outcome amounts 
5) all decisions modulated by mean EV 
6) all decisions modulated by gain amount  
7) all decisions modulated by safe amount  

```{r}

nTblock = 73;
nRun = 3;
offset = .6087;


# FIRST: let's make missed trial timing files for participants' runs that did not have any missed trials.

# index sub IDs who missed trials 
subsWhoMissed = unique(RDMraw$subjectIndex[is.na(RDMraw$choice)]); # list sub IDs who missed at least one trial
nSubWhoMissed = length(subsWhoMissed);

for (s in 1:nSubRaw) {
  # the way we are indexing for this loop is slightly different from above

  ind = grep(sprintf("sub-%s_run",subID_bids[s]), eventFiles); # get indices of event files for participant 
  RDMsub = RDMraw[RDMraw$subjectIndex==subNum[s],]; # load risky decision-making data
  
  # determine which runs have missed trials
  runsWithMissT = unique(RDMsub$block[is.na(RDMsub$choice)]);
  
  # if participant did not miss any trials across any runs:
  if (length(runsWithMissT)==0){
    noMissT = matrix(data=0, nrow=nTblock,ncol=3)
    
    missTrun1fileName = sprintf("%s/sub-%s/%s.txt", config$path$data$missedTrials_files,subID_bids[s],"noMissedTrials_run1");
    missTrun2fileName = sprintf("%s/sub-%s/%s.txt", config$path$data$missedTrials_files,subID_bids[s],"noMissedTrials_run2");
    missTrun3fileName = sprintf("%s/sub-%s/%s.txt", config$path$data$missedTrials_files,subID_bids[s],"noMissedTrials_run3");
    
    write.table(noMissT, file=missTrun1fileName, row.names = F, col.names = F, sep="\t");
    write.table(noMissT, file=missTrun2fileName, row.names = F, col.names = F, sep="\t");
    write.table(noMissT, file=missTrun3fileName, row.names = F, col.names = F, sep="\t");
    
  } else {
    
    runs = c(1,2,3);
    noMissRuns = runs[-c(runsWithMissT)]; # runs that have no missed trials
    
    if (length(noMissRuns)>0){
      for (m in 1:length(noMissRuns)){ # for all runs without a missed trial, make the 3-column zero timing files
        noMissT = matrix(data=0, nrow=nTblock, ncol=3)  
        missTrunFilename = sprintf("%s/sub-%s/noMissedTrials_run%s.txt", config$path$data$missedTrials_files,subID_bids[s], noMissRuns[m]);
        
        write.table(noMissT, file=missTrunFilename, row.names = F, col.names = F, sep="\t");
        
      } # for (m in 1:length(noMissRuns))
      
    }# if (length(noMissRuns)>0)
    
  } # if(length(runsWith...))
} # end for (s in 1:nSubRaw)



# Then for the TIMING FILES WHERE WE NEED TO ACCOUNT FOR MISSED TRIALS: we will make them based on the analysis we are interested in.

# CHOICE DISPLAY NO MODULATION:
for (s in 1:nSubWhoMissed) {  # for participants with missed trials
  
  # the way we are indexing for this loop is slightly different from above
  if (subsWhoMissed[s]>=10){
      sub_id_bid_format = sprintf("0%s", subsWhoMissed[s])
  } else {
      sub_id_bid_format = sprintf("00%s", subsWhoMissed[s])
  }
  
  
  ind = grep(sprintf("sub-%s_run",sub_id_bid_format), eventFiles); # get indices of event files for participant 

  #ind = grep(sub_id_bid_format,eventFiles)
  
  RDMsub = RDMraw[RDMraw$subjectIndex==subsWhoMissed[s],]; # load risky decision-making data
  
  # determine which runs have missed trials
  runsWithMissT = unique(RDMsub$block[is.na(RDMsub$choice)]);
  
  for (r in 1:length(runsWithMissT)){
    
    # determine which trials were missed within run
    missTind = RDMsub$triBlock[is.na(RDMsub$choice) & RDMsub$block==runsWithMissT[r]]
    
    eventrun = read.csv(eventFiles[ind[runsWithMissT[r]]]); # load event file for one run

    ###   CHOICE DISPLAY ###
    stimStartInd = which(eventrun$eventType=="stimulusStart");  # index start of stimulus display
    stimStartInd = stimStartInd[missTind]; # just need index for missed trials
    decWindowInd = which(eventrun$eventType=="decisionWindow"); # index start of decision window    
    decWindowInd = decWindowInd[missTind]; # just need index for missed trials
    
    # store events by onset, duration and modulation (mean ev, gain, safe) and mean center them (by functional run)
    onset = eventrun$onset[stimStartInd]; # onset is stimStart onset
    duration = eventrun$duration[stimStartInd] + eventrun$duration[decWindowInd]; # duration is stimStart duration + decisionWindow duration (which is basically RT)
    
    
     # Offset the onset times by .6087s (see notes above)
    onset = onset + offset;
    
    
    # store onset, duration and modulation into a single data frame
    choiceNoModulationMissT = cbind(onset, duration, 1); # gets a 1 for "weight" column since not using modulation here
    
     choiceNOMODmissTfileName = sprintf("%s/sub-%s/%s.txt", config$path$data$missedTrials_files,sub_id_bid_format,paste("missT_choiceDispNoMod_run",runsWithMissT[r],sep=""));
        
    # save files
    write.table(choiceNoModulationMissT, file=choiceNOMODmissTfileName, row.names = F, col.names = F, sep="\t");
    
    
  }# endfor (r in 1:nRun)
} # end for (s in 1:nSubRaw)

```


