---
title: "Desing Parameter Figures"
author: Hayley Brooks
output: html_notebook
---
***
##### Set up
```{r}
rm(list=ls());  # clear environment


library(config);
config <- config::get();

load("/Volumes/shlab/Projects/VNI/data/mriBehaviorClean/group_mriBehavior_clean.Rdata"); # mriBehClean data frame

library(lme4);
library(lmerTest);
```



##### Plot choice set
```{r}

singleSub = mriBehClean[mriBehClean$subjectIndex==5,];

# set colors by mean ev level (context)
singleSub$mEVcolor = "palegreen4"
singleSub$mEVcolor[singleSub$groundEV==10] = "lightsalmon2"
singleSub$mEVcolor[singleSub$groundEV==15] = "mediumpurple2"
singleSub$mEVcolor[singleSub$groundEV==20] = "goldenrod3"
singleSub$mEVcolor[singleSub$groundEV==25] = "royalblue1"

png("/Users/hayley/Documents/GitHub/vni/singleSubLevelsOfcontext.png")
plot(singleSub$riskyGain, singleSub$alternative, col=singleSub$mEVcolor, main="Five levels of context", ylab= "safe ($)", xlab="risky gain ($)", pch=16)
dev.off();

png("/Users/hayley/Documents/GitHub/vni/singleSubMeanEVacrossTask.png")
plot(singleSub$groundEV, pch=16, col=singleSub$mEVcolor, xlab="trial", ylab="mean EV", main="Context created by runs and shifts (mean EV)");
dev.off();

png("/Users/hayley/Documents/GitHub/vni/singleSubSafeacrossTask.png")
plot(singleSub$alternative, col=singleSub$mEVcolor, xlab="trial", ylab="safe ($)", main="Context created by runs and shifts (safe amt)", pch=16)
dev.off()


```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

