---
title: "Desing Parameter Figures"
author: Hayley Brooks
output: html_notebook
---
***
##### Set up
```{r}
rm(list=ls());  # clear environment


library(config);
config <- config::get();

load("/Volumes/shlab/Projects/VNI/data/mriBehaviorClean/group_mriBehavior_clean.Rdata"); # mriBehClean data frame

library(lme4);
library(lmerTest);
```



##### Plot choice set
```{r}

singleSub = mriBehClean[mriBehClean$subjectIndex==25,];

# set colors by mean ev level (context)
singleSub$mEVcolor = "palegreen4"
singleSub$mEVcolor[singleSub$groundEV==10] = "lightsalmon2"
singleSub$mEVcolor[singleSub$groundEV==15] = "mediumpurple2"
singleSub$mEVcolor[singleSub$groundEV==20] = "goldenrod3"
singleSub$mEVcolor[singleSub$groundEV==25] = "royalblue1"

# set some rho values for plotting
  yvals = seq(from=0,to=55,by=5);#  gain values
  rho = 2; #risk seeking
  xvalsSeekingH = (0.5*(yvals^rho))^(1/rho); # when the utility of the y value is equal to utility of x value
  rho = 1.5; #risk seeking
  xvalsSeekingL = (0.5*(yvals^rho))^(1/rho); # when the utility of the y value is equal to utility of x value
  rho = 0.5; #risk averse
  xvalsAverseL = (0.5*(yvals^rho))^(1/rho);
  rho = 0.75; #risk averse
  xvalsAverseH = (0.5*(yvals^rho))^(1/rho);
  xvalsNeutral = yvals*.5;

png("../singleSubLevelsOfcontext.png")

plot(xvalsNeutral,yvals,type='l', xlab = "safe", ylab="gain", ylim = c(0,60), xlim =c(0,30), col="black",lty = "longdash", axes=FALSE, main="Five levels of context"); #risk neutral


  lines(yvals,yvals,type='l', col="darkgrey",lty = "longdash"); # the limit; people will never gamble here
  lines(xvalsNeutral,yvals, col='black',lty = "longdash"); # someone who is risk seeking
  lines(xvalsSeekingH,yvals,col='black',lty = "longdash"); # someone who is risk seeking
  lines(xvalsSeekingL,yvals,col='black',lty = "longdash"); # someone who is risk seeking
  lines(xvalsAverseL,yvals,col='darkgrey',lty = "longdash"); # someone who is really risk averse
  lines(xvalsAverseH,yvals,col='black',lty = "longdash"); # someone who is risk averse


  points(singleSub$alternative, singleSub$riskyGain, col=singleSub$mEVcolor, ylab= "risky gain ($)", xlab="safe ($)", pch=16, cex=1.5)
axis(1, at =c(0, 5,10,15,20,25,30) , cex.lab=2, lwd=3)
axis(2, at =c(0, 10,20,30,40,50,60) , cex.lab=2, lwd=3)

dev.off();

png("../singleSubMeanEVacrossTask.png")
plot(singleSub$groundEV, pch=16, col=singleSub$mEVcolor, xlab="trial", ylab="mean EV", main="Context created by runs and shifts (mean EV)", axes=FALSE, cex=1.5);
axis(1, at =c(0,219) , cex.lab=2, lwd=3)
axis(2, at =c(0, 5,10,15,20,25) , cex.lab=2, lwd=3)
dev.off();

png("../singleSubSafeacrossTask.png")
plot(singleSub$alternative, col=singleSub$mEVcolor, xlab="trial", ylab="safe ($)", main="Context created by runs and shifts (safe amt)", pch=16, cex=1.5, axes=FALSE)
axis(1, at =c(0,219) , cex.lab=2, lwd=3)
axis(2, at =c(0, 5,10,15,20,25, 30) , cex.lab=2, lwd=3)
dev.off()


```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

